### 2020-02-19 phase2/report.tex
latex

\documentclass[twocolumn,11pt]{IEEEtran}
\usepackage[verbose,expansion=alltext,stretch=50]{microtype}

\title{Optimizing Scheduling Policies For Heterogeneous Distributed Systems}

\author{
   \begin{tabular}{c c c c}
       Mahmoud Adas & Evram Yousef & Mohamed Shawky & Remonda Talaat\\
       \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}} & \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}}
   \end{tabular}%
   \\
   \texttt{\small{\{mido3ds, evramyousef, mohamedshawky911, remondatalaat21\}@gmail.com}}
}%

\markboth{Cairo Uni. CMP Dep. OS, Research Phase 2, \today}{Shell}

\begin{document}
    \maketitle

    \begin{abstract}
        This is phase 2 of the research project.
        This paper describes the problem and explains why it is important.
        It also cites the most 3 papers with their critiques.
    \end{abstract}

    \section{Introduction}
    \IEEEPARstart{a}{} \emph{Heterogeneous System} is a system with multiple processors with some of them based on different instruction-set architecture (ISA) or micro-architecture. Usually, each processor excels at some aspect and performs poorly at another, and by combining them, we provide the best of each world. 
    Heterogeneous systems are more complex than homogeneous ones, because processors have different architectures. That means they need more complex scheduling policies to utilize the different properties efficiently.

    \section{The Problem}
    Our goal is to explore the possibility of providing more optimal scheduler policy for heterogeneous systems through 
    heuristic parameter optimization methods like different machine learning and/or genetic algorithms.
    We plan to build a simulation for some popular heterogeneous system, and integrate our optimization technique to 
    find better policy for different scenarios.

    \section{Why is it important?}
    Because heterogeneous systems are relatively new concept, they lack good support from OS developers, 
    and thus their schedulers policies still need more optimizations. 
    Recent findings show that they, the heterogeneous systems, can achieve lower energy delay product over homogeneous systems as much as 21\%-23\%. We assume that with more efficient scheduling they can achieve lower power consumption, and then they can become more economical.

    \section{References}
    \subsection*{[1] Alexandru Iulian Orhean,  Florin  Pop, and Ioan Raicu. New scheduling approach using reinforcement learning for heterogeneous distributed systems. Journal of Parallel and Distributed Computing, 117:292–302, 2018.}
    \begin{itemize}
        \item Why this paper: So we get insights into how to use machine learning in achieving better scheduling policies.
        \item Paper research problem: Heterogeneous systems task scheduling problem.
        \item Paper goal: Determining a more efficient scheduling policy for heterogeneous systems.
        \item Tools: BURLAP library, Java RMI API, remote allocated schedulers and WorkflowSim.
        \item Conclusion: The paper proposed a platform of scheduling solutions as a service based on machine learning agents. 
        And found out that reinforcement learning has the limitation of with more nodes the system was incapable of learning optimal policy.
    \end{itemize}

    \subsection*{[2] Rakesh Kumar, Er Rajiv Kumar, Er Sanjeev Gill, and Er Ashwani Kaushik. Genetic algorithm approach to operating system process scheduling problem. International journal of Engineering science and Technology, 2(9):4247–4252, 2010.}
    \begin{itemize}
        \item Why this paper: Because we plan to use GA as one of the methods of optimization, which what the paper used,
        even though the paper's target wasn't heterogeneous systems.
        \item Paper research problem: General-purpose OS task scheduling problem.
        \item Paper goal: Optimize scheduling parameters using GA.
        \item Conclusion: GA’s can provide a highly flexible and user-friendly, near optimal solution to the general job sequencing problem.
    \end{itemize}

    \subsection*{[3] Ashish Venkat and Dean M Tullsen. Harnessing isa diversity: Design  of  a  heterogeneous-isa  chip  multiprocessor. In 2014 ACM/IEEE 41st International Symposium on Computer Architecture(ISCA), pages 121–132. IEEE, 2014.}
    \begin{itemize}
        \item Why this paper: To understand heterogeneous systems structures.
        \item Paper research problem: Which one is more power effective, heterogeneous or homogeneous systems?
        \item Paper goal: prove heterogeneous systems are more power efficient
        \item Conclusion: heterogeneous systems improves energy efficiency over the most efficient single-ISA design by 23\%.
    \end{itemize} 
\end{document}

### 2020-02-20 phase2/report.tex
fixed abstract
fixed paper1

@@
    \begin{tabular}{c c c c}
-       Mahmoud Adas & Evram Yousef & Mohamed Shawky & Remonda Talaat\\
+       Mahmoud Adas & Evram Youssef & Mohamed Shawky & Remonda Talaat\\
        \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}} & \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}}
@@
         This paper describes the problem and explains why it is important.
-        It also cites the most 3 papers with their critiques.
+        It also cites 3 papers with their critiques.
     \end{abstract}
@@
         \item Conclusion: The paper proposed a platform of scheduling solutions as a service based on machine learning agents. 
-        And found out that reinforcement learning has the limitation of with more nodes the system was incapable of learning optimal policy.
+        And found out a limitation with reinforcement learning approach. Which was that the system was incapable of learning optimal policy after adding many nodes.
     \end{itemize}

### 2020-02-20 phase2/report.tex
added team number
edited proposal references

@@
 \author{
-   \begin{tabular}{c c c c}
+   \small{Team 10}
+
+   \begin{tabular}{c| c| c| c}
        Mahmoud Adas & Evram Youssef & Mohamed Shawky & Remonda Talaat\\
@@
    \end{tabular}%
-   \\
+
    \texttt{\small{\{mido3ds, evramyousef, mohamedshawky911, remondatalaat21\}@gmail.com}}
@@
 
-\markboth{Cairo Uni. CMP Dep. OS, Research Phase 2, \today}{Shell}
+\markboth{Cairo Uni. CMP Dep. | OS Research | Phase 2 | Team 10 | \today}{Shell}
 
@@
     \section{References}
-    \subsection*{[1] Alexandru Iulian Orhean,  Florin  Pop, and Ioan Raicu.
-New scheduling approach using reinforcement learning for heterogeneous distributed systems.
-Journal of Parallel and Distributed Computing, 117:292–302, 2018.}
-    \begin{itemize}
-        \item Why this paper: So we get insights into how to use machine learning in achieving better scheduling policies.
-        \item Paper research problem: Heterogeneous systems task scheduling problem.
-        \item Paper goal: Determining a more efficient scheduling policy for heterogeneous systems.
-        \item Tools: BURLAP library, Java RMI API, remote allocated schedulers and WorkflowSim.
-        \item Conclusion: The paper proposed a platform of scheduling solutions as a service based on machine learning agents. 
-        And found out a limitation with reinforcement learning approach. Which was that the system was incapable of learning optimal policy after adding many nodes.
-    \end{itemize}
-
-    \subsection*{[2] Rakesh Kumar, Er Rajiv Kumar, Er Sanjeev Gill, and Er Ashwani Kaushik.
-Genetic algorithm approach to operating system process scheduling problem.
-International journal of Engineering science and Technology, 2(9):4247–4252, 2010.}
-    \begin{itemize}
-        \item Why this paper: Because we plan to use GA as one of the methods of optimization, which what the paper used,
-        even though the paper's target wasn't heterogeneous systems.
-        \item Paper research problem: General-purpose OS task scheduling problem.
-        \item Paper goal: Optimize scheduling parameters using GA.
-        \item Conclusion: GA’s can provide a highly flexible and user-friendly, near optimal solution to the general job sequencing problem.
-    \end{itemize}
-
-    \subsection*{[3] Ashish Venkat and Dean M Tullsen.
+    \subsection*{[1] Ashish Venkat and Dean M Tullsen.
 Harnessing isa diversity: Design  of  a  heterogeneous-isa  chip  multiprocessor.
@@
     \end{itemize}
+
+     \subsection*{[2] Padole, Dr. Mamta \& Shah, Ankit. (2018). Comparative Study of Scheduling Algorithms in Heterogeneous Distributed Computing Systems.}
+    \begin{itemize}
+        \item Why this paper: To understand the concepts and concerns of scheduling in heterogeneous systems, as well as the recent algorithms.
+        \item Paper research problem: The recent scheduling algorithms for heterogeneous systems and their specifications.
+        \item Paper goal: The paper offers a hierarchical view of the static and dynamic scheduling algorithms found by then and gives an brief overview for each one. 
+        \item Conclusion: Most of the current scheduling algorithms can be further improved in various aspects, moreover static algorithms can be re-implemented to be dynamic.
+    \end{itemize}
+
+    \subsection*{[3] Arabnejad, Hamid \& Barbosa, Jorge.
+(2014).
+List Scheduling Algorithm for Heterogeneous Systems by an Optimistic Cost Table.
+IEEE Transactions on Parallel and Distributed Systems.}
+    \begin{itemize}
+        \item Why this paper: To get a sense of predictive scheduling in heterogeneous systems, as we will be using predictive models in our future work.
+        \item Paper research problem: Task scheduling in heterogeneous systems based on Optimistic Cost Table (OCT).
+        \item Paper goal: Achieve the same time complexity as the state-of-art methods, but with higher overall scheduling performance.
+        \item Conclusion: Predictive-Earliest-Finish-Time (PEFT) is outperforms Heterogeneous-Earliest-Finish-Time (HEFT) with the same time complexity.
+    \end{itemize} 
 \end{document}

### 2020-03-03 phase3/report.tex
added the second report

\documentclass[twocolumn,11pt]{IEEEtran}
\usepackage[verbose,expansion=alltext,stretch=50]{microtype}
\usepackage{graphicx}

\title{Optimizing Scheduling Policies For Heterogeneous Distributed Systems}

\author{

   \begin{tabular}{c| c| c| c}
       Mohamed Shawky & Remonda Talaat & Mahmoud Adas & Evram Youssef\\
       \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}} & \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}}
   \end{tabular}%

   \texttt{\small{\{mohamedshawky911, remondatalaat21, mido3ds, evramyousef\}@gmail.com}}
}%

\markboth{Cairo Uni. CMP Dep. | OS Research | Phase 3 | Team 10 | \today}{Shell}

\begin{document}
    \maketitle

    \begin{abstract}
        This is the second report of the research project.
        This report discusses our methodology for the proposed problem and our potential experiments.
    \end{abstract}

    \section{Introduction}
    \IEEEPARstart{T}{he} scheduling and resource allocation policies for a distributed system are very hard to achieve. This becomes even harder when the system is heterogeneous, where you have different types of chips. The problem is classified as \emph{NP Hard} and it's an open problem for research. Recursive optimization is one practical solution to reach a sub-optimal or even an optimal policy. In this work we will discuss several possible solutions to the problem and introduce yet a new idea that could potentially work better.

    \section{Formulation}
    To simulate the real heterogeneous systems, we have to create a simulation stub, where you have some defined machines with their specifications and a list of jobs that need to be executed on such machines. We will work with \emph{Global Static} scheduling scheme and the goal is to assign the jobs to the machines at each time step to maximize overall performance. Although resource utilization isn't our main concern, we may include it in our objective.

    \section{Methodology}

    \subsection{Baseline}
    First, let's discuss the baseline that all other experiments will be compare with. \emph{Heterogeneous Earliest Finish Time (HEFT)} will be considered as our baseline. \emph{(HEFT)} is an old well-established algorithm for scheduling in heterogeneous systems. Basically, the algorithm schedules a job on a machine based on job requirements with its earliest finish time. Although it's very simple, it's used as a comparison baseline for most of the research work made on this problem.

    \subsection{Genetic Algorithms}
    Our first attempt with recursive optimization for scheduling will be genetic algorithms. Genetic algorithms have proven to be very efficient in solving some of the hardest optimization problem. Previous work has been done in using genetic algorithms to solve scheduling problems. We will attempt using genetic algorithms to solve our proposed problem. The targeted \emph{fitness function} will be the average waiting time for all jobs.

    \subsection{Reinforcement Learning}
    Another possible solution is \emph{Reinforcement Learning (RL)}, which is one on the most dominant fields in optimization and decision making problems. The main advantage of \emph{RL} is that it can act in a very dynamic environment, so it can adapt to priority changes and deadlocks, for instance. Moreover, we can add extra layers of complexity to our problem, such as: adding a status to each machine which can change with time or machine-specific task which needs to be executed on a specific machine. However, this comes at a cost of complicated and unstable environment. \\
    If RL is to be used, one can consider using \emph{Q-Learning} to learn a scheduling policy using an environment of some machines.

    \subsection{Neural Networks (Deep Learning)}
    The main novel idea of this work will be the usage of \emph{neural networks} for the scheduling problem. \emph{Neural Networks} are known to be very good at learning representations and function approximation. In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.\\
    Previous work tried to use \emph{neural networks} to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}. However, we will try to make use of the recent advances in \emph{Deep Learning} to redefine the scheduling problem and solve it.

    \subsubsection{Architecture}
    Our architecture consists of two encoders and one decoder, as shown in Fig.\ref{fig:nn}. \\
    The first encoder is a simple feedforward fully connected network, to which is machines specifications are passed. This encoder learns a representation for the machines to be able to use it later in producing the outputs. \\
    The second encoder is an \emph{Recurrent Neural Network (RNN)}, to which the jobs are passed one by one ordered by the arrival time. This network learns a representation of the jobs preserving the arrival order. \\
    The representation of the jobs is later passed to an RNN decoder, which produces \emph{N} timesteps, at each step the processes currently running on each machine. The output is supported by attention modules to be able to take the machines representation into account when distributing the jobs.

    \begin{figure}[hp]
        \centering
        \includegraphics[width=0.45\textwidth]{sched_nn}
        \caption{The architecture of the proposed neural network for Heterogeneous systems scheduling}
        \label{fig:nn}
    \end{figure}

    \subsubsection{Objective Function}
    The cost function defined for this problem will be a simple \emph{mean square error (MSE)} between the output \emph{(processes/machine)} and some optimally solved examples.

    \subsubsection{Downsides}
    The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of jobs to be able to define the network. However, the network scheduling inference can be faster than many algorithms.

    \section{Experiments}
    This work will many focus of performance, specifically average waiting time and average turnaround time. 
    \begin{itemize}
        \item Measure the performance of \emph{HEFT} on our simulation stub.
        \item Experiment with Genetic Algorithms to explore possible improvements.
        \item Try the proposed neural network and explore the results and possible improvements.
        \item Experiment with \emph{RL} on our simulation stub. \emph{[OPTIONAL]}
    \end{itemize}

    \section{References}
    \subsection*{[1] Kumar, Ranjeet \& Dr.Rakesh, \& Er.Rajiv, \& Gill, Er \& Kaushik, Ashwani. (2010). Genetic Algorithm approach to Operating system process scheduling problem. International Journal of Engineering Science and Technology.}
    \begin{itemize}
        \item Why this paper: To explore the formulation of a scheduling problem using \emph{Genetic Algorithms}.
        \item Paper research problem: Operating systems process scheduling.
        \item Paper goal: To improve scheduling with \emph{Genetic Algorithms}.
        \item Conclusion: \emph{Genetic Algorithms} has a potential in such problems.
    \end{itemize}

     \subsection*{[2] Alexandru Iulian Orhean, Florin Pop, Ioan Raicu,
    New scheduling approach using reinforcement learning for heterogeneous distributed systems,
    Journal of Parallel and Distributed Computing.}
    \begin{itemize}
        \item Why this paper: To understand the scheduling problem as an \emph{RL} model.
        \item Paper research problem: \emph{RL} modelling for scheduling.
        \item Paper goal: Explore all layers of complexity of a scheduling problem using \emph{RL}.
        \item Conclusion: \emph{RL} can be very useful in dynamic scheduling.
    \end{itemize}

    \subsection*{[3] Chillet, Daniel \& Eiche, Antoine \& Pillement, Sébastien \& Sentieys, Olivier. (2011). Real-time scheduling on heterogeneous system-on-chip architectures using an optimised artificial neural network. Journal of Systems Architecture - Embedded Systems Design. 57. 340-353. 10.1016/j.sysarc.2011.01.004.}
    \begin{itemize}
        \item Why this paper: To explore the previous work made about the usage of neural networks in scheduling tasks.
        \item Paper research problem: Process scheduling with \emph{ANNs}.
        \item Paper goal: To improve the usage of neural networks in scheduling.
        \item Conclusion: Neural networks can be a good candidate for scheduling.
    \end{itemize}

\end{document}

### 2020-03-03 phase3/report.tex
edit porpose

@@
 \author{
-
    \begin{tabular}{c| c| c| c}
@@
 
-\markboth{Cairo Uni. CMP Dep. | OS Research | Phase 3 | Team 10 | \today}{Shell}
+\markboth{Cairo Uni. CMP Dep. $|$ OS Research $|$ Phase 3 $|$ Team 10 $|$ \today}{Shell}
 
@@
     \IEEEPARstart{T}{he} scheduling and resource allocation policies for a distributed system are very hard to achieve.
-This becomes even harder when the system is heterogeneous, where you have different types of chips.
-The problem is classified as \emph{NP Hard} and it's an open problem for research.
-Recursive optimization is one practical solution to reach a sub-optimal or even an optimal policy.
+This becomes even harder when the system is heterogeneous, where you have different architerctures of processors.
+The problem is classified as \emph{NP Hard} and it's \footnote{to the time of writing this paper, hopefully.} an open problem for research.
 In this work we will discuss several possible solutions to the problem and introduce yet a new idea that could potentially work better.
@@
 We will work with \emph{Global Static} scheduling scheme and the goal is to assign the jobs to the machines at each time step to maximize overall performance.
-Although resource utilization isn't our main concern, we may include it in our objective.
+
+    Although resources \footnote{the other resources of machine other than CPUs.} utilization isn't our main concern, we may include it in our objective.
 
@@
     \subsection{Baseline}
-    First, let's discuss the baseline that all other experiments will be compare with.
-\emph{Heterogeneous Earliest Finish Time (HEFT)} will be considered as our baseline.
-\emph{(HEFT)} is an old well-established algorithm for scheduling in heterogeneous systems.
-Basically, the algorithm schedules a job on a machine based on job requirements with its earliest finish time.
-Although it's very simple, it's used as a comparison baseline for most of the research work made on this problem.
+    We will consider \emph{Heterogeneous Earliest Finish Time} (HEFT) as our baseline and will compare its performance against our work.
 
-    \subsection{Genetic Algorithms}
-    Our first attempt with recursive optimization for scheduling will be genetic algorithms.
-Genetic algorithms have proven to be very efficient in solving some of the hardest optimization problem.
-Previous work has been done in using genetic algorithms to solve scheduling problems.
-We will attempt using genetic algorithms to solve our proposed problem.
-The targeted \emph{fitness function} will be the average waiting time for all jobs.
-
-    \subsection{Reinforcement Learning}
-    Another possible solution is \emph{Reinforcement Learning (RL)}, which is one on the most dominant fields in optimization and decision making problems.
-The main advantage of \emph{RL} is that it can act in a very dynamic environment, so it can adapt to priority changes and deadlocks, for instance.
-Moreover, we can add extra layers of complexity to our problem, such as: adding a status to each machine which can change with time or machine-specific task which needs to be executed on a specific machine.
-However, this comes at a cost of complicated and unstable environment.
-\\
-    If RL is to be used, one can consider using \emph{Q-Learning} to learn a scheduling policy using an environment of some machines.
+    HEFT is an old and well-established algorithm for scheduling in heterogeneous systems.
+Most research work compares their results with it because of its near-optimality.
+Basically, it chooses some process to run on some machine if the former has the earliest finish time, with considering the special nature of the heterogeneous system.
+HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process.
 
@@
     The main novel idea of this work will be the usage of \emph{neural networks} for the scheduling problem.
-\emph{Neural Networks} are known to be very good at learning representations and function approximation.
-In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.\\
-    Previous work tried to use \emph{neural networks} to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}.
+Neural Networks are known to be very good at learning representations and function approximation.
+In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.
+
+    Previous work tried to use neural networks to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}.
 However, we will try to make use of the recent advances in \emph{Deep Learning} to redefine the scheduling problem and solve it.
 
+    \subsection{Genetic Algorithms}
+    We will use genetic algorithms as a recursive optimization to solve our problem. The targeted \emph{fitness function} will be the average waiting time for all jobs.
+
+    Genetic algorithms have proven to be very efficient in solving some of the hardest optimization problem.
+Few similar research projects have been conducts in using genetic algorithms.
+We hope we can produce better results if the simulation and the algorithm were both well-tuned.
+
+    \subsection{Reinforcement Learning}
+    Another possible solution is \emph{Reinforcement Learning} (RL), which is one of the most dominant fields in optimization and decision making problems.
+
+    The main advantage of RL is that it can act in a very dynamic environment, so it can adapt, for instance, to priority changes and deadlocks.
+Moreover, we can add extra layers of complexity to our problem, such as: adding a status to each machine which can change with time or machine-specific tasks.
+However, this comes at a cost of complicated and unstable environment.
+
+    If RL is to be used, one can consider using \emph{Q-Learning} to learn a scheduling policy using an environment of some machines.
+
     \subsubsection{Architecture}
-    Our architecture consists of two encoders and one decoder, as shown in Fig.\ref{fig:nn}. \\
+    Our architecture consists of two encoders and one decoder, as shown in Fig.\ref{fig:nn}.
+
     The first encoder is a simple feedforward fully connected network, to which is machines specifications are passed.
 This encoder learns a representation for the machines to be able to use it later in producing the outputs.
-\\
+
     The second encoder is an \emph{Recurrent Neural Network (RNN)}, to which the jobs are passed one by one ordered by the arrival time.
 This network learns a representation of the jobs preserving the arrival order.
-\\
+
     The representation of the jobs is later passed to an RNN decoder, which produces \emph{N} timesteps, at each step the processes currently running on each machine.
@@
         \includegraphics[width=0.45\textwidth]{sched_nn}
-        \caption{The architecture of the proposed neural network for Heterogeneous systems scheduling}
+        \caption{The architecture of the proposed neural network for Heterogeneous systems scheduling.}
         \label{fig:nn}
@@
     \subsubsection{Objective Function}
-    The cost function defined for this problem will be a simple \emph{mean square error (MSE)} between the output \emph{(processes/machine)} and some optimally solved examples.
+    The cost function defined for this problem will be a simple \emph{mean square error} (MSE) between the output \emph{(processes/machine)} and some optimally solved examples.
 
@@
     \end{itemize} 
-
 \end{document}

### 2020-03-06 paper/paper.tex
branch merging

--- 2020-03-03 phase3/report.tex
@@
 
-\markboth{Cairo Uni. CMP Dep. | OS Research | Phase 3 | Team 10 | \today}{Shell}
+\markboth{Cairo Uni. CMP Dep. $|$ OS Research $|$ Final Paper $|$ \today}{Shell}
 
@@
     \begin{abstract}
-        This is the second report of the research project.
-        This report discusses our methodology for the proposed problem and our potential experiments.
+
     \end{abstract}
@@
     \section{Introduction}
-    \IEEEPARstart{T}{he} scheduling and resource allocation policies for a distributed system are very hard to achieve.
-This becomes even harder when the system is heterogeneous, where you have different types of chips.
-The problem is classified as \emph{NP Hard} and it's an open problem for research.
-Recursive optimization is one practical solution to reach a sub-optimal or even an optimal policy.
-In this work we will discuss several possible solutions to the problem and introduce yet a new idea that could potentially work better.
 
-    \section{Formulation}
-    To simulate the real heterogeneous systems, we have to create a simulation stub, where you have some defined machines with their specifications and a list of jobs that need to be executed on such machines.
-We will work with \emph{Global Static} scheduling scheme and the goal is to assign the jobs to the machines at each time step to maximize overall performance.
-Although resource utilization isn't our main concern, we may include it in our objective.
+    \section{Related Work}
 
@@
 
-    \subsection{Baseline}
-    First, let's discuss the baseline that all other experiments will be compare with.
-\emph{Heterogeneous Earliest Finish Time (HEFT)} will be considered as our baseline.
-\emph{(HEFT)} is an old well-established algorithm for scheduling in heterogeneous systems.
-Basically, the algorithm schedules a job on a machine based on job requirements with its earliest finish time.
-Although it's very simple, it's used as a comparison baseline for most of the research work made on this problem.
+    \section{Experimental Setup}
 
-    \subsection{Genetic Algorithms}
-    Our first attempt with recursive optimization for scheduling will be genetic algorithms.
-Genetic algorithms have proven to be very efficient in solving some of the hardest optimization problem.
-Previous work has been done in using genetic algorithms to solve scheduling problems.
-We will attempt using genetic algorithms to solve our proposed problem.
-The targeted \emph{fitness function} will be the average waiting time for all jobs.
+    \section{Discussion and Results}
 
-    \subsection{Reinforcement Learning}
-    Another possible solution is \emph{Reinforcement Learning (RL)}, which is one on the most dominant fields in optimization and decision making problems.
-The main advantage of \emph{RL} is that it can act in a very dynamic environment, so it can adapt to priority changes and deadlocks, for instance.
-Moreover, we can add extra layers of complexity to our problem, such as: adding a status to each machine which can change with time or machine-specific task which needs to be executed on a specific machine.
-However, this comes at a cost of complicated and unstable environment.
-\\
-    If RL is to be used, one can consider using \emph{Q-Learning} to learn a scheduling policy using an environment of some machines.
-
-    \subsection{Neural Networks (Deep Learning)}
-    The main novel idea of this work will be the usage of \emph{neural networks} for the scheduling problem.
-\emph{Neural Networks} are known to be very good at learning representations and function approximation.
-In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.\\
-    Previous work tried to use \emph{neural networks} to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}.
-However, we will try to make use of the recent advances in \emph{Deep Learning} to redefine the scheduling problem and solve it.
-
-    \subsubsection{Architecture}
-    Our architecture consists of two encoders and one decoder, as shown in Fig.\ref{fig:nn}. \\
-    The first encoder is a simple feedforward fully connected network, to which is machines specifications are passed.
-This encoder learns a representation for the machines to be able to use it later in producing the outputs.
-\\
-    The second encoder is an \emph{Recurrent Neural Network (RNN)}, to which the jobs are passed one by one ordered by the arrival time.
-This network learns a representation of the jobs preserving the arrival order.
-\\
-    The representation of the jobs is later passed to an RNN decoder, which produces \emph{N} timesteps, at each step the processes currently running on each machine.
-The output is supported by attention modules to be able to take the machines representation into account when distributing the jobs.
-
-    \begin{figure}[hp]
-        \centering
-        \includegraphics[width=0.45\textwidth]{sched_nn}
-        \caption{The architecture of the proposed neural network for Heterogeneous systems scheduling}
-        \label{fig:nn}
-    \end{figure}
-
-    \subsubsection{Objective Function}
-    The cost function defined for this problem will be a simple \emph{mean square error (MSE)} between the output \emph{(processes/machine)} and some optimally solved examples.
-
-    \subsubsection{Downsides}
-    The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of jobs to be able to define the network.
-However, the network scheduling inference can be faster than many algorithms.
-
-    \section{Experiments}
-    This work will many focus of performance, specifically average waiting time and average turnaround time. 
-    \begin{itemize}
-        \item Measure the performance of \emph{HEFT} on our simulation stub.
-        \item Experiment with Genetic Algorithms to explore possible improvements.
-        \item Try the proposed neural network and explore the results and possible improvements.
-        \item Experiment with \emph{RL} on our simulation stub. \emph{[OPTIONAL]}
-    \end{itemize}
+    \section{Conclusion}
 
     \section{References}
-    \subsection*{[1] Kumar, Ranjeet \& Dr.Rakesh, \& Er.Rajiv, \& Gill, Er \& Kaushik, Ashwani.
-(2010).
-Genetic Algorithm approach to Operating system process scheduling problem.
-International Journal of Engineering Science and Technology.}
-    \begin{itemize}
-        \item Why this paper: To explore the formulation of a scheduling problem using \emph{Genetic Algorithms}.
-        \item Paper research problem: Operating systems process scheduling.
-        \item Paper goal: To improve scheduling with \emph{Genetic Algorithms}.
-        \item Conclusion: \emph{Genetic Algorithms} has a potential in such problems.
-    \end{itemize}
-
-     \subsection*{[2] Alexandru Iulian Orhean, Florin Pop, Ioan Raicu,
-    New scheduling approach using reinforcement learning for heterogeneous distributed systems,
-    Journal of Parallel and Distributed Computing.}
-    \begin{itemize}
-        \item Why this paper: To understand the scheduling problem as an \emph{RL} model.
-        \item Paper research problem: \emph{RL} modelling for scheduling.
-        \item Paper goal: Explore all layers of complexity of a scheduling problem using \emph{RL}.
-        \item Conclusion: \emph{RL} can be very useful in dynamic scheduling.
-    \end{itemize}
-
-    \subsection*{[3] Chillet, Daniel \& Eiche, Antoine \& Pillement, Sébastien \& Sentieys, Olivier.
-(2011).
-Real-time scheduling on heterogeneous system-on-chip architectures using an optimised artificial neural network.
-Journal of Systems Architecture - Embedded Systems Design.
-57.
-340-353.
-10.1016/j.sysarc.2011.01.004.}
-    \begin{itemize}
-        \item Why this paper: To explore the previous work made about the usage of neural networks in scheduling tasks.
-        \item Paper research problem: Process scheduling with \emph{ANNs}.
-        \item Paper goal: To improve the usage of neural networks in scheduling.
-        \item Conclusion: Neural networks can be a good candidate for scheduling.
-    \end{itemize}
 

### 2020-03-06 development/gen_prcoess.py

@@ -1,0 +1,43 @@
+import numpy as np
+from numpy.random import normal, poisson
+import argparse
+import json
+
+parser = argparse.ArgumentParser()
+parser.add_argument('configuration')
+args = parser.parse_args()
+
+
+class NpEncoder(json.JSONEncoder):
+    def default(self, obj):
+        if isinstance(obj, np.integer):
+            return int(obj)
+        elif isinstance(obj, np.floating):
+            return float(obj)
+        elif isinstance(obj, np.ndarray):
+            return obj.tolist()
+        else:
+            return super(NpEncoder, self).default(obj)
+
+
+with open(args.configuration, 'r') as f:
+    inp = json.load(f)
+
+    n = int(inp['num_processes'])
+    μ_arr, σ_arr = inp['arrival']['mean'], inp['arrival']['spread']
+    μ_burst, σ_burst = inp['burst']['mean'], inp['burst']['spread']
+    λ = inp['memory_poisson_lambda']
+
+    ariv_times = normal(μ_arr, σ_arr, n)
+    burst_times = normal(μ_burst, σ_burst, n)
+    memory = poisson(λ, n)
+
+    proc = []
+    for i in range(1, n+1):
+        proc.append({
+            'proc_num': i,
+            'arriv_time': ariv_times[i-1],
+            'burst_time': burst_times[i-1],
+            'memory': memory[i-1]
+        })
+    print(json.dumps(proc, cls=NpEncoder, indent=4))

### 2020-03-06 development/schedulers/nn/data_preparation/main.c

@@ -1,0 +1,354 @@
+/*******************************************************
+	    HEFT DUPLICATION IMPLEMENTATION
+********************************************************/
+//NOTES
+//UPPER RANK ARRAY(tasks_upper_rank[]) INITIALIZED TO -1 SO AS TO PREVENT REDUNDANT CALCULATION OF UPPER RANKS
+//COMMUNICATION COST MATRIX(data[][]) HAS -1 VALUE FOR NON COMMUNICATING TASKS
+
+
+#include<stdio.h>
+#include<stdlib.h>
+int no_tasks,no_machines;
+double **computation_costs,**data_transfer_rate,**data,*tasks_upper_rank;
+int *sorted_tasks;
+
+struct TaskProcessor
+{
+    int processor;
+    double AST;
+    double AFT;
+};
+
+struct TaskProcessor *schedule;
+/*******************************************************
+	FUNCTION FOR DETERMINATION OF UPPER RANK
+********************************************************/
+// Calculate average communication cost and give feed to sorted task array
+void insertinto(int task,double rank)
+{
+    static int pos;
+    int i;
+    for(i=pos-1; i>=0; i--)
+        if(rank>tasks_upper_rank[sorted_tasks[i]])
+            sorted_tasks[i+1]=sorted_tasks[i];
+        else
+            break;
+    sorted_tasks[i+1]=task;
+    pos++;
+}
+
+// Calculate the average cost of communication between source and destination
+double avg_communicationcost(int source,int destination)
+{
+    int i,j;
+    double avg=0.0;
+    for(i=0; i<no_machines; i++)
+        for(j=0; j<no_machines; j++)
+        {
+            if(data_transfer_rate[i][j]!=0)
+                avg+=(data[source][destination]/data_transfer_rate[i][j]);
+        }
+    avg=avg/(no_machines*no_machines-no_machines);
+    return avg;
+}
+
+// Calculate the upper rank
+double calculate_upper_rank(int task)
+{
+    int j;
+    double avg_communication_cost,successor,avg=0.0,max=0,rank_successor;
+
+    for(j=0; j<no_machines; j++)
+        avg+=computation_costs[task][j];
+    avg/=no_machines;
+
+    for(j=0; j<no_tasks; j++)
+    {
+        // Check if node(j) is a successor of node(task)
+        if(data[task][j]!=-1)
+        {
+            avg_communication_cost=avg_communicationcost(task,j);
[…]

### 2020-03-06 development/schedulers/nn/model.py

@@ -1,0 +1,124 @@
+from __future__ import print_function
+import torch 
+import torch.nn as nn
+import torch.nn.functional as F
+
+class JobEncoder(nn.Module):
+    """
+        Implementation of the encoder network for jobs.
+    """
+    def __init__(self, input_dim, enc_hid_dim, dec_dim):
+        """
+            initialization method
+
+            Parameters:
+            input_dim(int): number of input features to the RNN cell.
+            enc_hid_dim(int): number of hidden units for the RNN cell.
+            dec_dim(int): number of units in the decoder network, usually equal to the maximum number of jobs.
+        """
+        super(JobEncoder, self).__init__()
+        
+        self.rnn = nn.GRU(input_dim, enc_hid_dim, bidirectional = True)
+        
+        self.fc = nn.Linear(enc_hid_dim * 2, dec_dim)
+        
+    def forward(self, input):
+        """
+            forward propagation method
+
+            Parameters:
+            input(Tensor): input to the RNN layers.
+
+            Returns:
+            outputs(Tensor): outputs of the RNN layers.
+            hidden(Tensor): hidden units of the last two layers.
+        """
+        outputs, hidden = self.rnn(input)
+
+        hidden = torch.tanh(self.fc(torch.cat((hidden[-2,:,:], hidden[-1,:,:]), dim = 1)))
+
+        return outputs, hidden
+
+class MachineEncoder(nn.Module):
+    """
+        Implementation of the encoder network for machines.
+    """
+    def __init__(self, input_dim, input_features, dec_dim):
+        """
+            initialization method
+
+            Parameters:
+            input_dim(int): number of inputs for the encoder, equal to the number of machines.
+            input_features(int): number of features for each input.
+            dec_dim(int): number of units in the decoder network, usually equal to the maximum number of jobs.
+        """
+        super(MachineEncoder, self).__init__()
+        
+        self.conv1d = nn.Conv1d(input_features, 1, kernel_size=1, stride=1, padding=0)
+
+        self.fc = nn.Linear(input_dim, dec_dim)
+        
+    def forward(self, input):
+        """
+            forward propagation method
+
+            Parameters:
+            input(Tensor): input to the conv1d layer
+
+            Returns:
+            outputs(Tensor): outputs of the fully connected layer
+        """
+        outputs =  self.conv1d(input)
+
[…]

### 2020-03-06 development/sim.py

@@ -1,0 +1,109 @@
+import sys
+import os
+import copy
+import json
+import argparse
+
+
+class Process:
+    num: int = 0
+    arriv_time: float = 0
+    burst_time: float = 0
+    memory: float = 0
+
+    @staticmethod
+    def from_json(path: str):
+        procs = []
+
+        with open(path, 'r') as f:
+            for pr in json.load(f):
+                p = Process()
+                p.num = int(pr['proc_num'])
+                p.arriv_time = float(pr['arriv_time'])
+                p.burst_time = float(pr['burst_time'])
+                p.memory = float(pr['memory'])
+
+                procs.append(p)
+
+        return procs
+
+
+class Machine:
+    cpus: int  # num of CPUs, a soft constraint
+    memory: float  # in GB
+
+    @staticmethod
+    def from_json(path: str):
+        with open(path, 'r') as f:
+            json_machine = json.load(f)
+
+            m = Machine()
+            m.cpus = int(json_machine['cpus'])
+            m.memory = float(json_machine['memory'])
+
+            return m
+
+
+class SimulationInput:
+    prcs: [Process] = []  # array of processes
+    machine: Machine = Machine()
+    context_switch_time: float = 0
+    time_quant: float = 0  # RR
+
+    @staticmethod
+    def build(processes_path: str, machine_path: str, cont_switch: float, time_quant: float):
+        inp = SimulationInput()
+
+        # sort processes with arrival time
+        inp.prcs = sorted(Process.from_json(processes_path),
+                          key=lambda x: x.arriv_time)
+
+        inp.context_switch_time = cont_switch
+        inp.time_quant = time_quant
+        inp.machine = Machine.from_json(machine_path)
+
+        return inp
+
+
+class SimulationOutput:
+    # for each process (1, 2, .. n)
+    waiting_times: [float] = []
+    turnaround_times: [float] = []
+    weighted_turnaround_times: [float] = []
+
+    def print(self):
+        json_output = {'waiting_times': self.waiting_times,
+                       'turnaround_times': self.turnaround_times,
+                       'weighted_turnaround_times': self.weighted_turnaround_times,
+                       'average_turnaround': sum(self.turnaround_times)/len(self.turnaround_times),
+                       'average_weighted_turnaround': sum(self.weighted_turnaround_times)/len(self.weighted_turnaround_times)}
+        print(json.dumps(json_output, indent=4))
+
+
+def simulate(inp: SimulationInput) -> SimulationOutput:
+    out = SimulationOutput()
+
[…]

### 2020-03-06 development/schedulers/nn/data_preparation/main.c
added data sample and data preparation

@@ -1,354 +1,0 @@
-/*******************************************************
-	    HEFT DUPLICATION IMPLEMENTATION
-********************************************************/
-//NOTES
-//UPPER RANK ARRAY(tasks_upper_rank[]) INITIALIZED TO -1 SO AS TO PREVENT REDUNDANT CALCULATION OF UPPER RANKS
-//COMMUNICATION COST MATRIX(data[][]) HAS -1 VALUE FOR NON COMMUNICATING TASKS
-
-
-#include<stdio.h>
-#include<stdlib.h>
-int no_tasks,no_machines;
-double **computation_costs,**data_transfer_rate,**data,*tasks_upper_rank;
-int *sorted_tasks;
-
-struct TaskProcessor
-{
-    int processor;
-    double AST;
-    double AFT;
-};
-
-struct TaskProcessor *schedule;
-/*******************************************************
-	FUNCTION FOR DETERMINATION OF UPPER RANK
-********************************************************/
-// Calculate average communication cost and give feed to sorted task array
-void insertinto(int task,double rank)
-{
-    static int pos;
-    int i;
-    for(i=pos-1; i>=0; i--)
-        if(rank>tasks_upper_rank[sorted_tasks[i]])
-            sorted_tasks[i+1]=sorted_tasks[i];
-        else
-            break;
-    sorted_tasks[i+1]=task;
-    pos++;
-}
-
-// Calculate the average cost of communication between source and destination
-double avg_communicationcost(int source,int destination)
-{
-    int i,j;
-    double avg=0.0;
-    for(i=0; i<no_machines; i++)
-        for(j=0; j<no_machines; j++)
-        {
-            if(data_transfer_rate[i][j]!=0)
-                avg+=(data[source][destination]/data_transfer_rate[i][j]);
-        }
-    avg=avg/(no_machines*no_machines-no_machines);
-    return avg;
-}
-
-// Calculate the upper rank
-double calculate_upper_rank(int task)
-{
-    int j;
-    double avg_communication_cost,successor,avg=0.0,max=0,rank_successor;
-
-    for(j=0; j<no_machines; j++)
-        avg+=computation_costs[task][j];
-    avg/=no_machines;
-
-    for(j=0; j<no_tasks; j++)
-    {
-        // Check if node(j) is a successor of node(task)
-        if(data[task][j]!=-1)
-        {
-            avg_communication_cost=avg_communicationcost(task,j);
[…]

### 2020-03-06 development/schedulers/nn/model.py
added data sample and data preparation

@@ -88,7 +88,7 @@ class SchedNN(nn.Module):
             max_jobs(int): maximum number of jobs.
             rnn_hid_dim(int): number of hidden units in the RNN layers.
             machine_dim(int): number of data features for each machine [num_cores, core_freq, mem_cap].
-            job_dim(int): number of data features for each job [arrival_time, burst_time, mem_util, deadline].
+            job_dim(int): number of data features for each job [arrival_time, avg_burst_time, mem_util, priority].
         """
         super(SchedNN, self).__init__()
 

### 2020-03-06 development/schedulers/nn/data_loader/dataloader.py
added dataset class

@@ -1,0 +1,65 @@
+from torch.utils.data import Dataset 
+import torchvision.transforms as transform
+import torch
+import pandas as pd
+import numpy as np  
+import os
+
+class SchedDataset(Dataset):
+    """
+        Implementation of the custom dataset for scheduling data.
+    """
+    def __init__(self, machines_path, jobs_dir, results_dir):
+        """
+            initialization method
+
+            Parameters:
+            machines_path(string): path to the csv file that contains machines information.
+            jobs_dir(string): directory of jobs lists.
+            results_dir(string): directory of scheduling results.
+        """
+        self.jobs_list = os.listdir(jobs_dir)
+        self.results_list = os.listdir(results_dir)
+
+        self.machines_list = pd.read_csv(machines_path)
+        del self.machines_list["machine_id"]
+
+        self.machines_list = torch.from_numpy(self.machines_list.to_numpy())
+
+    def __getitem__(self, idx):
+        """
+            returns a single dataset item
+
+            Parameters:
+            idx(int): index of required dataset item.
+
+            Returns:
+            machines_list(Tensor): machines information tensor.
+            job_list(Tensor): job information tesnor.
+            out_machines(Tensor): machines running each job in the list.
+            out_time(Tensor): start and finish time of each job in the list.
+        """
+        job_list = pd.read_csv(self.jobs_list[idx])
+        del job_list["job_id"]
+
+        job_list = torch.from_numpy(job_list.to_numpy())
+
+        out_list = pd.read_csv(self.results_list[idx])
+        del out_list["job_id"]
+
+        out_list = torch.from_numpy(out_list.to_numpy())
+
+        out_machines = out_list[:,0]
+
+        out_time = out_list[:,1:]
+
+        return self.machines_list, job_list, out_machines, out_time
+
+    def __len__(self):
+        """
+            returns the length of the dataset
+
+            Returns:
+            length(int): length of dataset items.
+        """
+        return len(self.jobs_list)

### 2020-03-06 development/schedulers/nn/inference.py
added trainer and inference scripts

@@ -1,0 +1,45 @@
+from data_loader.dataloader import SchedDataset
+from model import SchedNN
+import torch.nn as nn
+from torch.utils.data import DataLoader
+import numpy as np
+import argparse
+import torch
+import math
+
+def main(args=None):
+    parser = argparse.ArgumentParser(description=__doc__)
+    
+    parser.add_argument('--machines_path', help='Path to the machines csv.', type=str, default="data/machines/machines.csv")
+    parser.add_argument('--jobs_dir', help='Path to the jobs csvs.', type=str, default="data/jobs/")
+    parser.add_argument('--results_dir', help='Path to the results csvs.', type=str, default="data/schedules/")
+    parser.add_argument('--model_path', help='Path to the trained model file.', type=str, default="checkpoints/final_model_100.pt")
+    parser.add_argument('--batch_size', help='Batch size.', type=int, default=8)
+
+    args = parser.parse_args(args)
+    
+    device = "cuda:0" if torch.cuda.is_available else "cpu"
+
+    dataset = SchedDataset(args.machines_path, args.jobs_dir, args.results_dir)
+    dataloader = DataLoader(dataset, batch_size=args.batch_size, shuffle=True, num_workers=4)
+    data_iterator = iter(dataloader)
+
+    model = torch.load(args.model_path)
+
+    model.eval()
+
+    steps_num = int(math.ceil(len(dataset)/ args.batch_size))
+
+    print("The model contains: {} parameters".format(sum(p.numel() for p in model.parameters())))
+
+    for step in range(steps_num):
+        X_machine, X_job, Y_machine, Y_time = next(data_iterator)
+        X_machine = X_machine.to(device)
+        X_job = X_job.to(device)
+        out_machine, out_time = model(X_machine, X_job)
+        print("Saving output #{} ...".format(step))
+        np.save("data/outputs/{}_machines.npy".format(step), out_machine)
+        np.save("data/outputs/{}_times.npy".format(step), out_time)
+
+if __name__ == '__main__':
+    main()

### 2020-03-06 development/schedulers/nn/trainer.py

@@ -1,0 +1,61 @@
+from data_loader.dataloader import SchedDataset
+from model import SchedNN
+import torch.nn as nn
+from torch.utils.data import DataLoader
+import argparse
+import torch
+import math
+
+def main(args=None):
+    parser = argparse.ArgumentParser(description=__doc__)
+    
+    parser.add_argument('--machines_path', help='Path to the machines csv.', type=str, default="data/machines/machines.csv")
+    parser.add_argument('--jobs_dir', help='Path to the jobs csvs.', type=str, default="data/jobs/")
+    parser.add_argument('--results_dir', help='Path to the results csvs.', type=str, default="data/schedules/")
+    parser.add_argument('--batch_size', help='Batch size.', type=int, default=8)
+    parser.add_argument('--num_epochs', help='Number of epochs.', type=int, default=100)
+
+    args = parser.parse_args(args)
+    
+    device = "cuda:0" if torch.cuda.is_available else "cpu"
+
+    dataset = SchedDataset(args.machines_path, args.jobs_dir, args.results_dir)
+    dataloader = DataLoader(dataset, batch_size=args.batch_size, shuffle=True, num_workers=4)
+    data_iterator = iter(dataloader)
+
+    model = SchedNN().to(device)
+
+    print("The model contains: {} parameters.".format(sum(p.numel() for p in model.parameters())))
+
+    optimizer = torch.optim.Adam(model.parameters(), lr=1e-4)
+    scheduler = torch.optim.lr_scheduler.StepLR(optimizer, step_size=15, gamma=0.5)
+
+    criterion_1 = nn.MSELoss()
+    criterion_2 = nn.CrossEntropyLoss()
+
+    steps_per_epoch = int(math.ceil(len(dataset)/ args.batch_size))
+
+    for epoch in range(1,args.num_epochs+1):
+        loss_per_epoch = 0
+        for step in range(steps_per_epoch):
+            X_machine, X_job, Y_machine, Y_time = next(data_iterator)
+            X_machine = X_machine.to(device)
+            X_job = X_job.to(device)
+            Y_machine = Y_machine.to(device)
+            Y_time = Y_time.to(device)
+            optimizer.zero_grad()
+            out_machine, out_time = model(X_machine, X_job)
+            loss = criterion_1(out_machine, Y_machine) + criterion_2(out_time, Y_time)
+            loss.backward()
+            optimizer.step()
[…]

### 2020-03-06 development/schedulers/nn/inference.py
added device detach to inference.py

@@ -38,8 +38,8 @@ def main(args=None):
         X_job = X_job.to(device)
         out_machine, out_time = model(X_machine, X_job)
         print("Saving output #{} ...".format(step))
-        np.save("data/outputs/{}_machines.npy".format(step), out_machine)
-        np.save("data/outputs/{}_times.npy".format(step), out_time)
+        np.save("data/outputs/{}_machines.npy".format(step), out_machine.cpu().detach().numpy())
+        np.save("data/outputs/{}_times.npy".format(step), out_time.cpu().detach().numpy())
 
 if __name__ == '__main__':
     main()

### 2020-03-06 development/schedulers/nn/data_loader/dataloader.py
training nn scheduler

@@ -9,7 +9,7 @@ class SchedDataset(Dataset):
     """
         Implementation of the custom dataset for scheduling data.
     """
-    def __init__(self, machines_path, jobs_dir, results_dir):
+    def __init__(self, machines_path, jobs_dir, results_dir, max_job_dim=485):
         """
             initialization method
 
@@ -18,8 +18,12 @@ class SchedDataset(Dataset):
             jobs_dir(string): directory of jobs lists.
             results_dir(string): directory of scheduling results.
         """
+        self.max_job_dim = max_job_dim
         self.jobs_list = os.listdir(jobs_dir)
         self.results_list = os.listdir(results_dir)
+
+        self.jobs_list = [os.path.join(jobs_dir, dir) for dir in self.jobs_list]
+        self.results_list = [os.path.join(results_dir, dir) for dir in self.results_list]
 
         self.machines_list = pd.read_csv(machines_path)
         del self.machines_list["machine_id"]
@@ -43,17 +47,25 @@ class SchedDataset(Dataset):
         del job_list["job_id"]
 
         job_list = torch.from_numpy(job_list.to_numpy())
+        out_job_list = torch.zeros(self.max_job_dim, job_list.shape[1])
+        out_job_list[:job_list.shape[0],:] = job_list
 
         out_list = pd.read_csv(self.results_list[idx])
         del out_list["job_id"]
 
         out_list = torch.from_numpy(out_list.to_numpy())
+        out_out_list = torch.zeros(self.max_job_dim, out_list.shape[1])
+        out_out_list[:out_list.shape[0],:] = out_list
 
-        out_machines = out_list[:,0]
+        out_machines = out_out_list[:,0]
+        out_time = out_out_list[:,1:]
 
-        out_time = out_list[:,1:]
+        out_machines_list = torch.t(self.machines_list).to(dtype=torch.float)
+        out_job_list = out_job_list.to(dtype=torch.float)
+        out_machines = torch.t(out_machines)
+        out_time = torch.t(out_time).to(dtype=torch.float)
 
-        return self.machines_list, job_list, out_machines, out_time
+        return out_machines_list, out_job_list, out_machines, out_time
 
     def __len__(self):
         """

### 2020-03-06 development/schedulers/nn/model.py

@@ -111,9 +111,11 @@ class SchedNN(nn.Module):
             Returns:
             Tensor: n timesteps with scheduled jobs for each machine.
         """    
-        machine_features = self.job_enc(machine_input)
+        job_input = torch.transpose(job_input, 1, 0)
 
-        job_features = self.job_enc(job_input)
+        machine_features = self.machine_enc(machine_input)
+
+        _, job_features = self.job_enc(job_input)
 
         feature_fusion = torch.stack([machine_features, job_features], dim=1)
 

### 2020-03-06 development/schedulers/nn/trainer.py

@@ -13,22 +13,29 @@ def main(args=None):
     parser.add_argument('--jobs_dir', help='Path to the jobs csvs.', type=str, default="data/jobs/")
     parser.add_argument('--results_dir', help='Path to the results csvs.', type=str, default="data/schedules/")
     parser.add_argument('--batch_size', help='Batch size.', type=int, default=8)
+    parser.add_argument('--learning_rate', help='Learning rate.', type=float, default=1e-5)
     parser.add_argument('--num_epochs', help='Number of epochs.', type=int, default=100)
+    parser.add_argument('--max_jobs', help='Maximum number of jobs.', type=int, default=485)
+    parser.add_argument('--num_machines', help='Number of machines to be used.', type=int, default=123)
+    parser.add_argument('--rnn_hid_dim', help='Number of hidden units in encoder RNN.', type=int, default=16)
+    parser.add_argument('--machine_dim', help='Number of features per machine.', type=int, default=3)
+    parser.add_argument('--job_dim', help='Number of features per job.', type=int, default=4)
 
     args = parser.parse_args(args)
     
     device = "cuda:0" if torch.cuda.is_available else "cpu"
 
-    dataset = SchedDataset(args.machines_path, args.jobs_dir, args.results_dir)
+    dataset = SchedDataset(args.machines_path, args.jobs_dir, args.results_dir, args.max_jobs)
     dataloader = DataLoader(dataset, batch_size=args.batch_size, shuffle=True, num_workers=4)
     data_iterator = iter(dataloader)
 
-    model = SchedNN().to(device)
+    model = SchedNN(max_jobs=args.max_jobs, num_machines=args.num_machines, rnn_hid_dim=args.rnn_hid_dim, \
+                    machine_dim=args.machine_dim, job_dim=args.job_dim).to(device)
 
     print("The model contains: {} parameters.".format(sum(p.numel() for p in model.parameters())))
 
-    optimizer = torch.optim.Adam(model.parameters(), lr=1e-4)
-    scheduler = torch.optim.lr_scheduler.StepLR(optimizer, step_size=15, gamma=0.5)
+    optimizer = torch.optim.Adam(model.parameters(), lr=args.learning_rate)
+    scheduler = torch.optim.lr_scheduler.StepLR(optimizer, step_size=20, gamma=0.5)
 
     criterion_1 = nn.MSELoss()
     criterion_2 = nn.CrossEntropyLoss()
@@ -45,7 +52,9 @@ def main(args=None):
[…]

### 2020-03-07 development/schedulers/ga/genetic_algorithm.py
genetic algorithms initialization

@@ -1,0 +1,40 @@
+import random
+
+class Job:
+    def __init__(self, id, burst_time, priority, dependencies=None):
+        """
+            Initializes the job with the appropriate information
+        """
+        if not dependencies:
+            dependencies = []
+
+        self.id = id
+        self.burst_time = burst_time
+        self.priority = priority
+        self.dependencies = dependencies
+        self.min_completion_time = -1
+
+    def is_dependency_of(self, other):
+        """
+            Returns true if this task is a dependency (direct or indirect) of other
+        """
+        return (self in other.dependencies) or any(self.is_dependency_of(task) for task in other.dependencies)
+
+    def get_min_completion_time(self):
+        """
+           Returns the minimum completion time of this task based on the minimum completion times of its dependencies
+        """
+        if self.min_completion_time < 0:
+            self.min_completion_time = self.duration
+            if len(self.dependencies) > 0:
+                self.min_completion_time += max(
+                    [task.get_min_completion_time() for task in self.dependencies])
+        return self.min_completion_time
+
+    def __repr__(self):
+        """
+            Returns the represetation of the job
+        """
+        return '<Job %s>' % self.identifier
+
+

### 2020-03-07 development/gen_prcoess.py
removed simulation stub

@@ -1,43 +1,0 @@
-import numpy as np
-from numpy.random import normal, poisson
-import argparse
-import json
-
-parser = argparse.ArgumentParser()
-parser.add_argument('configuration')
-args = parser.parse_args()
-
-
-class NpEncoder(json.JSONEncoder):
-    def default(self, obj):
-        if isinstance(obj, np.integer):
-            return int(obj)
-        elif isinstance(obj, np.floating):
-            return float(obj)
-        elif isinstance(obj, np.ndarray):
-            return obj.tolist()
-        else:
-            return super(NpEncoder, self).default(obj)
-
-
-with open(args.configuration, 'r') as f:
-    inp = json.load(f)
-
-    n = int(inp['num_processes'])
-    μ_arr, σ_arr = inp['arrival']['mean'], inp['arrival']['spread']
-    μ_burst, σ_burst = inp['burst']['mean'], inp['burst']['spread']
-    λ = inp['memory_poisson_lambda']
-
-    ariv_times = normal(μ_arr, σ_arr, n)
-    burst_times = normal(μ_burst, σ_burst, n)
-    memory = poisson(λ, n)
-
-    proc = []
-    for i in range(1, n+1):
-        proc.append({
-            'proc_num': i,
-            'arriv_time': ariv_times[i-1],
-            'burst_time': burst_times[i-1],
-            'memory': memory[i-1]
-        })
-    print(json.dumps(proc, cls=NpEncoder, indent=4))

### 2020-03-07 development/sim.py

@@ -1,109 +1,0 @@
-import sys
-import os
-import copy
-import json
-import argparse
-
-
-class Process:
-    num: int = 0
-    arriv_time: float = 0
-    burst_time: float = 0
-    memory: float = 0
-
-    @staticmethod
-    def from_json(path: str):
-        procs = []
-
-        with open(path, 'r') as f:
-            for pr in json.load(f):
-                p = Process()
-                p.num = int(pr['proc_num'])
-                p.arriv_time = float(pr['arriv_time'])
-                p.burst_time = float(pr['burst_time'])
-                p.memory = float(pr['memory'])
-
-                procs.append(p)
-
-        return procs
-
-
-class Machine:
-    cpus: int  # num of CPUs, a soft constraint
-    memory: float  # in GB
-
-    @staticmethod
-    def from_json(path: str):
-        with open(path, 'r') as f:
-            json_machine = json.load(f)
-
-            m = Machine()
-            m.cpus = int(json_machine['cpus'])
-            m.memory = float(json_machine['memory'])
-
-            return m
-
-
-class SimulationInput:
-    prcs: [Process] = []  # array of processes
-    machine: Machine = Machine()
-    context_switch_time: float = 0
-    time_quant: float = 0  # RR
-
-    @staticmethod
-    def build(processes_path: str, machine_path: str, cont_switch: float, time_quant: float):
-        inp = SimulationInput()
-
-        # sort processes with arrival time
-        inp.prcs = sorted(Process.from_json(processes_path),
-                          key=lambda x: x.arriv_time)
-
-        inp.context_switch_time = cont_switch
-        inp.time_quant = time_quant
-        inp.machine = Machine.from_json(machine_path)
-
-        return inp
-
-
-class SimulationOutput:
-    # for each process (1, 2, .. n)
-    waiting_times: [float] = []
-    turnaround_times: [float] = []
-    weighted_turnaround_times: [float] = []
-
-    def print(self):
-        json_output = {'waiting_times': self.waiting_times,
-                       'turnaround_times': self.turnaround_times,
-                       'weighted_turnaround_times': self.weighted_turnaround_times,
-                       'average_turnaround': sum(self.turnaround_times)/len(self.turnaround_times),
-                       'average_weighted_turnaround': sum(self.weighted_turnaround_times)/len(self.weighted_turnaround_times)}
-        print(json.dumps(json_output, indent=4))
-
-
-def simulate(inp: SimulationInput) -> SimulationOutput:
-    out = SimulationOutput()
-
[…]

### 2020-03-17 development/ga_scheduler/genetic_algorithm.py
complete genetic scheduler

@@ -1,5 +1,14 @@
 import random
 
+# Global Constants
+POPULATION_SIZE = 10
+REPRODUCE_PROBABILITY = 0.5
+MUTATION_PROBABILITY = 0.1
+TOTAL_TIME_WEIGHT = 0.8
+PRIORITY_FLOWTIME_WEIGHT = 0.2
+
+
+# Job Encapsulating Class
 class Job:
     def __init__(self, id, burst_time, priority, dependencies=None):
         """
@@ -25,7 +34,7 @@ class Job:
            Returns the minimum completion time of this task based on the minimum completion times of its dependencies
         """
         if self.min_completion_time < 0:
-            self.min_completion_time = self.duration
+            self.min_completion_time = self.burst_time
             if len(self.dependencies) > 0:
                 self.min_completion_time += max(
                     [task.get_min_completion_time() for task in self.dependencies])
@@ -35,6 +44,327 @@ class Job:
         """
             Returns the represetation of the job
         """
-        return '<Job %s>' % self.identifier
+        return '<Job %s>' % self.id
 
 
+# Schedule Encapulating Class
+class Schedule:
+    def __init__(self, processor_schedules=None):
+        """
+            Initializes the schedule with the appropriate information
+        """
+        if not processor_schedules:
+            processor_schedules = []
+        self.processor_schedules = processor_schedules
+        self.task_completion_map = {}
+        self.task_dependency_set_map = {}
+
+    def min_processor_schedule_length(self):
+        """
+        Returns the number of tasks in the smallest processor
+        """
+        return min([len(processor) for processor in self.processor_schedules])
+
+    def has_unique_tasks(self):
+        """
+        Returns true if the schedule does not have more than one of the same task
+        """
+        task_set = set()
+        task_sum = 0
+        for processor in self.processor_schedules:
+            task_set.update(processor)
+            task_sum += len(processor)
+        return len(task_set) == task_sum
+
+    def has_direct_dependency_violation(self):
+        """
+        Returns true if in any processor, a task is executed before one of its dependencies
+        """
+        for processor in self.processor_schedules:
+            for i in range(len(processor)):
+                for dependency in processor[i].dependencies:
+                    if dependency in processor[i+1:]:
+                        return True
+        return False
+
+    def get_task_location(self, task):
+        """
+        Returns the processor and task indices of any given task, None if the task is not in this schedule
+        """
+        for i in range(len(self.processor_schedules)):
[…]

### 2020-03-17 development/ga_scheduler/schedule.py

@@ -1,0 +1,60 @@
+import argparse
+import json
+
+import genetic_algorithm
+
+def main():
+    """
+        genetic scheduling driver function
+    """
+    # Get arguments
+    argparser = argparse.ArgumentParser(description=__doc__)
+    argparser.add_argument('--data_path', type=str, default='data/jobs.json',
+                            help='path to data json')
+    args = argparser.parse_args()                        
+
+    # Get data
+    with open(args.data_path) as f:
+        data = json.load(f)
+
+    raw_tasks = data['tasks']
+    tasks = []
+    for task in raw_tasks:
+        dependencies = task['depend']
+        if dependencies:
+            dependencies = [dependencies]
+
+        t = genetic_algorithm.Job(task['id'], task['length'], task['priority'], dependencies)
+        tasks.append(t)
+
+    # Setup dependencies
+    for task in tasks:
+        dependencies = []
+        for depend_id in task.dependencies:
+            for t2 in tasks:
+                if t2.id == depend_id:
+                    dependencies.append(t2)
+                    break
+            else:
+                raise Exception('Invalid dependency')
+        task.dependencies = dependencies
+
+    constraints = data['constraints']
+
+    processors = constraints['processors']
+    generations = constraints['generations']
+    total_time = constraints['total_time']
+
+    gen_alg = genetic_algorithm.GeneticTaskScheduler(tasks)
+    schedule = gen_alg.schedule_tasks(processors, generations, total_time)
+
+    # Display the schedule
+    for i, processor in enumerate(schedule):
+        print(f"Processor #{i} ...")
+        for j, task in enumerate(processor):
+            if task:
+                print(task)
+
+
+if __name__ == "__main__":
+    main()

### 2020-03-18 paper/paper.tex
Introduction + Related Work

@@
 
-\title{Optimizing Scheduling Policies For Heterogeneous Distributed Systems}
+\title{DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems}
 
@@
 \begin{abstract}
-
+To be conducted, once the results are complete.  
 \end{abstract}
@@
 
+\IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) have driven our needs for better resource allocation methods.
+The performance of any system critically depends on the algorithms used to schedule tasks on its resources. 
+The general objective is to get the best possible performance with the reasonable resource utilization.
+Recently, the heterogeneity of the computational systems are increasing, due to the nature of the applications.
+\\
+A \emph{heterogeneous system}\cite{venkat2014harnessing} can be defined as a range of resources, different in underlying architecture.
+The usage of a heterogeneous system has proven to be very efficient in increasing the system performance and reducing the overall power consumption.
+However, this comes with the problem of complex task scheduling.
+The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system because of the different execution rates of processors and different communication rates among different processors.
+The parameters of such problem make it very suitable for various optimization techniques.
+Previous work has investigated the usage of techniques such as genetic algorithms\cite{article2} to solve the task scheduling problem.
+\\
+In this paper, we investigate the ability of \emph{neural networks} to learn a representation of static local task scheduling problem.
+The recent advances in \emph{Deep Learning} research is used to build our scheduling system.
+\emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is used as a target, where the network learns to approximate its performance.
+Also, we include a genetic algorithm experiment for the same problem for comparison.
+We will discuss our approach to the problem and its limitations.
+
 \section{Related Work}
+
+Since task scheduling in heterogeneous systems is a wide problem, a lot of research has been conducted in this area. Various techniques have been introduced for the problem. 
+\emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is one of the most well-established algorithms for task scheduling in heterogeneous systems. 
+It's a local static scheduling algorithms, which deals with a \emph{Direct Acyclic Graph} (DAG) of jobs displaying the dependencies between different processes.
+Each job has a running time for each different machine and a time for communicating the results to children jobs.
+A wide range of algorithms\cite{inbook} follows HEFT further improving the scheduling performance. \\
+Recent research has been conducted to use optimization algorithms and predictive models to schedule tasks on heterogeneous system, since these algorithms have proven to be very efficient in solving complex computational problems.
+\emph{Genetic algorithms}\cite{article2} can be used to efficiently schedule tasks in different systems.
+Also, \emph{Reinforcement Learning} (RL)\cite{ORHEAN2018292} has been a strong candidate for the problem, as the scheduling problem can be formulated as an \emph{RL} problem, solved by various \emph{RL} techniques.
+Some papers also investigated the usage of \emph{Artificial Neural Networks} (ANN)\cite{article3} in task scheduling in heterogeneous systems. \\ 
+In this paper, we make use of recent advances in \emph{Deep Learning} and build a deep representation of the scheduling problem using \emph{Recurrent Neural Networks}(RNNs)\cite{chung2014empirical} and other techniques.
 
@@
 
-    \section{References}
+\medskip
+
+\bibliographystyle{unsrt}
+\bibliography{paper}
 

### 2020-03-23 paper/paper.tex
added final methodology section

@@
 Since task scheduling in heterogeneous systems is a wide problem, a lot of research has been conducted in this area. Various techniques have been introduced for the problem. 
+The scheduling algorithms for heterogeneous distributed systems are divided into two main categories based on their target metric.
+Application-Specific scheduling targets job execution speed (performance).
+System-Specific targets resource utilization.
+\\
 \emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is one of the most well-established algorithms for task scheduling in heterogeneous systems. 
-It's a local static scheduling algorithms, which deals with a \emph{Direct Acyclic Graph} (DAG) of jobs displaying the dependencies between different processes.
-Each job has a running time for each different machine and a time for communicating the results to children jobs.
+It's a local static scheduling algorithms, which deals with a \emph{Direct Acyclic Graph} (DAG) of tasks displaying the dependencies between different processes.
+Each task has a running time for each different machine and a time for communicating the results to children tasks.
 A wide range of algorithms\cite{inbook} follows HEFT further improving the scheduling performance. \\
@@
 \section{Methodology}
+
+\subsection{Formulation}
+First, let us specify the main target of this work.
+As the task scheduling in heterogeneous distributed system is a vast field with lots of settings and algorithms\cite{inbook}, we choose our scheduling setting to be local and static.
+The goal of this work is to explore the ability of neural networks to approximate the performance of some well-established scheduling algorithms.
+In our setting, the algorithms are provided a list of tasks, each has its own execution time on different machines and a set of heterogeneous machines, on which the tasks are executed.
+We compare the results neural networks to some other heuristic and approximate methods.
+\\
+Although, we choose local static scheduling, we assume that the neural approximation methods can work in other settings as well.
+
+\subsection{Baseline}
+Two baseline methods are considered.
+We choose \emph{Heterogeneous Earliest Finish Time} (HEFT)\cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems.
+Also, genetic algorithms\cite{article2} is provided as an approximate baseline.
+
+\subsubsection{Heterogeneous Earliest Time First (HEFT)}
+HEFT\cite{993206} is an old and well-established algorithm for scheduling in heterogeneous systems.
+It has been used as a baseline in research due to its near-optimal results.
+Basically, it chooses some process to run on some machine, if the former has the earliest finish time, with considering the special nature of the heterogeneous system.
+However, HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process.
+
+\subsubsection{Genetic Algorithms}
+Genetic algorithms\cite{article2} have proven to be very efficient in solving some of the hardest optimization problem.
+Previous work on the use of genetic algorithms in task scheduling \cite{article2} is adapted to the heterogeneous setting by adding parameters for execution time of different tasks on different machines.
+\\
+The targeted \emph{fitness function} will be the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
+\begin{equation}
+\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N}
+\end{equation}
+
+\subsection{Neural Networks (Deep Learning)}
+The main novel idea of this work is the use of \emph{neural networks} for the scheduling problem.
+Neural Networks are known to be very good at learning representations and function approximation.
+In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.
+\\
+Previous work tried to use neural networks to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}\cite{article3}.
+However, we try to make use of the recent advances in \emph{Deep Learning} to redefine the scheduling problem and solve it.
+\\
+As mentioned, The provided input is a list of tasks with its information and a set of machines.
+We want the network to learn an implicit representation of the given tasks and machines.
+Then, the network learn the mapping between the learned representation and the desired schedule.
+In other words, the target of the network is to take two input list of information of both tasks and machines and then output for each task, the machine to be executed on, the actual start time and the actual finish time.
+
+\subsubsection{Architecture}
+Our architecture consists of two encoders and one decoder, as shown in Fig.\ref{fig:nn}. \\
+The first encoder is a fully convolutional network of \emph{1D} convolutional layers, to which is machines specifications are passed.
+This encoder learns a representation for the machines to be able to use it later in producing the outputs.
+\\
+The second encoder is an \emph{Recurrent Neural Network} (RNN)\cite{chung2014empirical}, to which the tasks are passed one by one ordered by the arrival time.
+This network learns a representation of the tasks preserving the arrival order.
+RNN is chosen due to its proven effectiveness in dealing with sequential data.
+\\
+The two representations are then stacked and passed to two modules.
+A classification module which states the machine on which a specific task is executed.
+A regression module that identifies the actual start time and the actual finish time.
+Mainly, the two modules consist of \emph{1D} convolutional layers.
+
+\begin{figure}[hp]
+    \centering
+    \includegraphics[width=0.45\textwidth]{sched_nn}
+    \caption{The architecture of the proposed neural network for distributed heterogeneous systems scheduling}
+    \label{fig:nn}
+\end{figure}
+
+\subsubsection{Objective Function}
+The cost function defined for this architecture is a sum of two criteria.
+Categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$.
+So it can be summarized as follows:
+\begin{equation}
+\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t)
+\end{equation}
+where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range.
+
+\subsubsection{Downsides}
+The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network.
+These numbers are used to define the network and loss function dimensions.
 

### 2020-04-09 paper/paper.tex
introduction refine

@@
 The performance of any system critically depends on the algorithms used to schedule tasks on its resources.
-The general objective is to get the best possible performance with the reasonable resource utilization.
-Recently, the heterogeneity of the computational systems are increasing, due to the nature of the applications.
+These systems contain limited resources, that should be allocated properly, in order to perform the required tasks with maximum efficiency avoiding starvation and resource exhaustion.
+The general objective of any scheduling technique is to get the best possible performance with a reasonable resource utilization. \\
+
+Recently, the heterogeneity of the computational systems has increased tremendously, due to the nature of the applications and the great advances in IoT and distributed systems.
+A \emph{heterogeneous system} can be defined as a range of resources, different in underlying architecture, targeting different types of computational tasks.
+The usage of a heterogeneous system has proven to be very efficient in increasing the system performance and reducing the overall power consumption.
+Recent studies \cite{venkat2014harnessing} show that \emph{heterogeneous system} can outperform the best homogeneous systems by as much as 21\%, with 23\% energy savings and
+a reduction of 32\% in Energy Delay Product. These numbers can be improved even more with better task scheduling and resource allocation methods. \\
+
+However, this comes with the problem of complex task scheduling.
+The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system, because of the different execution rates of processors and different communication rates among different processors, which add extra layers of complexity to the problem.
 \\
-A \emph{heterogeneous system}\cite{venkat2014harnessing} can be defined as a range of resources, different in underlying architecture.
-The usage of a heterogeneous system has proven to be very efficient in increasing the system performance and reducing the overall power consumption.
-However, this comes with the problem of complex task scheduling.
-The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system because of the different execution rates of processors and different communication rates among different processors.
+
 The parameters of such problem make it very suitable for various optimization techniques.
-Previous work has investigated the usage of techniques such as genetic algorithms\cite{article2} to solve the task scheduling problem.
+Recursive optimization techniques are very efficient in solving many optimization problem.
+Previous work has investigated the usage of techniques such as \emph{genetic algorithms} \cite{article2} to solve the task scheduling problem.
+Also, the usage of a progressive decision making techniques such as \emph{Reinforcement Learning} \cite{ORHEAN2018292} for task scheduling in heterogeneous systems has been investigated.
 \\
-In this paper, we investigate the ability of \emph{neural networks} to learn a representation of static local task scheduling problem.
-The recent advances in \emph{Deep Learning} research is used to build our scheduling system.
+
+In this paper, we investigate the ability of advanced predictive models to learn a representation of static local task scheduling problem.
+This learned representation will be used to approximate the scheduling performance of other scheduling techniques.
+\emph{Neural Networks} are our best candidate for this task.
+Neural networks are being used in many fields replacing traditional methods, such as image classification \cite{10.1145/3065386}, object detection \cite{ren2015faster}, neural language modelling \cite{ren2015faster}, image generation \cite{karras2019analyzing} and others.
+They have proven to be more efficient than other traditional methods.
+The complexity of the neural networks comes in the development phases, where the network is designed and trained.
+However, in inference phase, neural networks can achieve very accurate results at high speed.
+Recent work has been done on optimizing neural network inference through various techniques, such as  \cite{choukroun2019lowbit} and pruning \cite{yeom2019pruning}.
+\\
+
+The recent advances in \emph{Deep Learning} research is considered in designing and training our scheduling network.
 \emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is used as a target, where the network learns to approximate its performance.

### 2020-04-09 paper/paper.tex
related work refine

@@
 However, in inference phase, neural networks can achieve very accurate results at high speed.
-Recent work has been done on optimizing neural network inference through various techniques, such as  \cite{choukroun2019lowbit} and pruning \cite{yeom2019pruning}.
+Recent work has been done on optimizing neural network inference through various techniques, such as quantization \cite{choukroun2019lowbit} and pruning \cite{yeom2019pruning}.
 \\
@@
 The recent advances in \emph{Deep Learning} research is considered in designing and training our scheduling network.
-\emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is used as a target, where the network learns to approximate its performance.
+\emph{Heterogeneous Earliest Time First} (HEFT) \cite{993206} is used as a target, where the network learns to approximate its performance.
 Also, we include a genetic algorithm experiment for the same problem for comparison.
@@
 
-Since task scheduling in heterogeneous systems is a wide problem, a lot of research has been conducted in this area. Various techniques have been introduced for the problem. 
-The scheduling algorithms for heterogeneous distributed systems are divided into two main categories based on their target metric.
-Application-Specific scheduling targets job execution speed (performance).
-System-Specific targets resource utilization.
-\\
-\emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is one of the most well-established algorithms for task scheduling in heterogeneous systems. 
+Since task scheduling in heterogeneous systems is a wide problem, a lot of research has been conducted in this area.
+Various techniques have been introduced for the problem.
+These techniques are categorized based on multiple aspects \cite{inbook} and some of which are adapted from task scheduling methods for homogeneous systems.
+
+\subsection{Scheduling Categories}
+In this work, we focus on three basic categorization of heterogeneous task scheduling methods.
+
+\subsubsection{Application-Specific vs. System-Specific}
+Heterogeneous scheduling methods can be divided into two main categories based on their target metric.\\
+\emph{Application-Specific} scheduling targets task execution speed (performance), where scheduling
+decisions are determined based on many parameters including application performance, task inter-dependency and the availability of resources.
+\emph{System-Specific} targets resource utilization, where scheduling decisions are based on the percentage of time a resource is available or busy.
+
+\subsubsection{Global vs. Local}
+Also, heterogeneous scheduling methods can be divided into global and local scheduling.
+\emph{Global} scheduling can migrate the tasks from one processor to another, meanwhile \emph{local} scheduling can't migrate, so once a task is assigned to a processor, it stays in its queue.
+
+\subsubsection{Static vs. Dynamic}
+Finally, heterogeneous scheduling methods can be divided into static and dynamic scheduling.
+In \emph{static} scheduling, the tasks required to be scheduled are defined before scheduling.
+However, in \emph{dynamic} scheduling, new tasks can be introduced during the scheduling process
+
+\subsection{Heterogeneous Earliest Time First (HEFT)}
+HEFT \cite{993206} is one of the most well-established algorithms for task scheduling in heterogeneous systems.
 It's a local static scheduling algorithms, which deals with a \emph{Direct Acyclic Graph} (DAG) of tasks displaying the dependencies between different processes.
 Each task has a running time for each different machine and a time for communicating the results to children tasks.
-A wide range of algorithms\cite{inbook} follows HEFT further improving the scheduling performance. \\
+A wide range of algorithms \cite{inbook} follows HEFT further improving the scheduling performance.
+
+\subsection{Optimization Algorithms}
 Recent research has been conducted to use optimization algorithms and predictive models to schedule tasks on heterogeneous system, since these algorithms have proven to be very efficient in solving complex computational problems.
-\emph{Genetic algorithms}\cite{article2} can be used to efficiently schedule tasks in different systems.
-Also, \emph{Reinforcement Learning} (RL)\cite{ORHEAN2018292} has been a strong candidate for the problem, as the scheduling problem can be formulated as an \emph{RL} problem, solved by various \emph{RL} techniques.
-Some papers also investigated the usage of \emph{Artificial Neural Networks} (ANN)\cite{article3} in task scheduling in heterogeneous systems. \\ 
-In this paper, we make use of recent advances in \emph{Deep Learning} and build a deep representation of the scheduling problem using \emph{Recurrent Neural Networks}(RNNs)\cite{chung2014empirical} and other techniques.
+\subsubsection{Genetic Algorithms (GA)}
+GA \cite{article2} can be used to efficiently schedule tasks in different systems.
+It's used for static scheduling, where a fixed population of tasks are scheduled recursively on multiple processors, based on a specific fitness function.
+\subsubsection{Reinforcement Learning (RL)}
+Also, RL \cite{ORHEAN2018292} has been a strong candidate for the problem, as the scheduling problem can be formulated as an \emph{RL} problem, solved by various \emph{RL} techniques.
+RL techniques are effective in solving progressive decision making problems, so they are more likely to be used in dynamic scheduling.
+
+\subsection{Neural Networks}
+Recent advances in \emph{Deep Learning} have enabled neural networks to dominate many fields, such as computer vision, natural language processing and others.
+Neural networks are able to perform perception tasks at a human-level accuracy.
+Also, neural networks are very efficient in function approximation and representation learning.
+These properties make neural networks a perfect choice for massive scale automation of many tasks.
+Some studies even investigated the usage of \emph{Artificial Neural Networks} (ANN)\cite{article3} in task scheduling in heterogeneous systems.
+Most of these studies focus on the usage of \emph{Hopfield Nets} and \emph{Inhibitor Neurons} \cite{article3}.
+\\
+
+In this paper, we make use of recent advances in \emph{Deep Learning} and build a deep representation of the scheduling problem and use it to approximate the performance of heterogeneous scheduling methods.
+\emph{Recurrent Neural Networks}(RNNs) \cite{chung2014empirical} are used for this purpose, as they have the ability to learn complex temporal information from a time-series data, which is exactly our case.
+Other network operations to be used, too.
 

### 2020-04-09 paper/paper.tex
methodology refine

@@
 Some studies even investigated the usage of \emph{Artificial Neural Networks} (ANN)\cite{article3} in task scheduling in heterogeneous systems.
-Most of these studies focus on the usage of \emph{Hopfield Nets} and \emph{Inhibitor Neurons} \cite{article3}.
+Most of these studies focus on the usage of \emph{Hopfield Nets} \cite{sathasivam2008logic} and \emph{Inhibitor Neurons} \cite{article3}.
 \\
@@
 
+\subsection{Motivation}
+Heterogeneous task scheduling is a relatively new concept, which lacks developers support.
+It's an active area of research, where many techniques are being developed through time.
+Being able to achieve the best possible performance on the given tasks, while keeping good utilization of resources is a tedious problem in heterogeneous systems.
+Aside from being accurate, the scheduling methods have to be fast in its execution, also they should not consume the system resources.
+
+Heterogeneous scheduling methods are very computationally expensive.
+However, neural networks are relatively fast in inference and research is being conducted on optimizing inference even more.
+So, if a neural network can approximate the performance of current scheduling method, it can replace this method in production.
+
+In this work, we study the ability of neural networks to approximate some heuristic methods and explore its accuracy and execution time against heuristic and approximated methods.
+
 \subsection{Formulation}
 First, let us specify the main target of this work.
-As the task scheduling in heterogeneous distributed system is a vast field with lots of settings and algorithms\cite{inbook}, we choose our scheduling setting to be local and static.
+As the task scheduling in heterogeneous distributed system is a vast field with lots of settings and algorithms \cite{inbook}, we choose our scheduling setting to be local and static.
 The goal of this work is to explore the ability of neural networks to approximate the performance of some well-established scheduling algorithms.
@@
 We compare the results neural networks to some other heuristic and approximate methods.
-\\
+
 Although, we choose local static scheduling, we assume that the neural approximation methods can work in other settings as well.
@@
 Two baseline methods are considered.
-We choose \emph{Heterogeneous Earliest Finish Time} (HEFT)\cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems.
-Also, genetic algorithms\cite{article2} is provided as an approximate baseline.
+We choose \emph{Heterogeneous Earliest Finish Time} (HEFT) \cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems.
+Also, genetic algorithms \cite{article2} is provided as an approximate baseline.
+\\
 
 \subsubsection{Heterogeneous Earliest Time First (HEFT)}
-HEFT\cite{993206} is an old and well-established algorithm for scheduling in heterogeneous systems.
+HEFT \cite{993206} is an old and well-established algorithm for scheduling in heterogeneous systems.
 It has been used as a baseline in research due to its near-optimal results.
 Basically, it chooses some process to run on some machine, if the former has the earliest finish time, with considering the special nature of the heterogeneous system.
-However, HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process.
+However, HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process \\
 
 \subsubsection{Genetic Algorithms}
-Genetic algorithms\cite{article2} have proven to be very efficient in solving some of the hardest optimization problem.
+Genetic algorithms \cite{article2} have proven to be very efficient in solving some of the hardest optimization problem.
 Previous work on the use of genetic algorithms in task scheduling \cite{article2} is adapted to the heterogeneous setting by adding parameters for execution time of different tasks on different machines.
-\\
+
 The targeted \emph{fitness function} will be the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
@@
 In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.
-\\
-Previous work tried to use neural networks to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}\cite{article3}.
+\emph{Offline Optimization} of neural networks is to be used, in order to be able to train the network on scheduling samples and then use the trained network to do inference.
+We avoid using \emph{online optimization}, as it's slow and we mainly care about execution time of the scheduling method.
+
+Previous work tried to use neural networks to solve scheduling problem through \emph{Hopfield Nets} \cite{sathasivam2008logic} and \emph{Inhibitor Neurons} \cite{article3}.
 However, we try to make use of the recent advances in \emph{Deep Learning} to redefine the scheduling problem and solve it.
-\\
+
 As mentioned, The provided input is a list of tasks with its information and a set of machines.
@@
 In other words, the target of the network is to take two input list of information of both tasks and machines and then output for each task, the machine to be executed on, the actual start time and the actual finish time.
+\\
 
@@
 This encoder learns a representation for the machines to be able to use it later in producing the outputs.
-\\
-The second encoder is an \emph{Recurrent Neural Network} (RNN)\cite{chung2014empirical}, to which the tasks are passed one by one ordered by the arrival time.
+
+The second encoder is an \emph{Recurrent Neural Network} (RNN) \cite{chung2014empirical}, to which the tasks are passed one by one ordered by the arrival time.
 This network learns a representation of the tasks preserving the arrival order.
-RNN is chosen due to its proven effectiveness in dealing with sequential data.
-\\
+RNN is chosen due to its proven effectiveness in dealing with sequential data, as they can learn complex temporal information from time sequences.
+
 The two representations are then stacked and passed to two modules.
@@
 \end{equation}
-where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range.
+where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range. \\
 

### 2020-04-09 paper/core/introduction.tex
section split into files

--- 2020-04-09 paper/paper.tex
@@
-\documentclass[twocolumn,11pt]{IEEEtran}
-\usepackage[verbose,expansion=alltext,stretch=50]{microtype}
-\usepackage{graphicx}
-
-\title{DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems}
-
-\author{
-   \begin{tabular}{c| c| c| c}
-       Mohamed Shawky & Remonda Talaat & Mahmoud Adas & Evram Youssef\\
-       \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}} & \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}}
-   \end{tabular}%
-
-   \texttt{\small{\{mohamedshawky911, remondatalaat21, mido3ds, evramyousef\}@gmail.com}}
-}%
-
-\markboth{Cairo Uni. CMP Dep. $|$ OS Research $|$ Final Paper $|$ \today}{Shell}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-To be conducted, once the results are complete.  
-\end{abstract}
-
-\section{Introduction}
-
 \IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) have driven our needs for better resource allocation methods.
@@
 The recent advances in \emph{Deep Learning} research is considered in designing and training our scheduling network.
-\emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is used as a target, where the network learns to approximate its performance.
+\emph{Heterogeneous Earliest Time First} (HEFT) \cite{993206} is used as a target, where the network learns to approximate its performance.
 Also, we include a genetic algorithm experiment for the same problem for comparison.
 We will discuss our approach to the problem and its limitations.
-
-\section{Related Work}
-
-Since task scheduling in heterogeneous systems is a wide problem, a lot of research has been conducted in this area. Various techniques have been introduced for the problem. 
-The scheduling algorithms for heterogeneous distributed systems are divided into two main categories based on their target metric.
-Application-Specific scheduling targets job execution speed (performance).
-System-Specific targets resource utilization.
-\\
-\emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is one of the most well-established algorithms for task scheduling in heterogeneous systems. 
-It's a local static scheduling algorithms, which deals with a \emph{Direct Acyclic Graph} (DAG) of tasks displaying the dependencies between different processes.
-Each task has a running time for each different machine and a time for communicating the results to children tasks.
-A wide range of algorithms\cite{inbook} follows HEFT further improving the scheduling performance. \\
-Recent research has been conducted to use optimization algorithms and predictive models to schedule tasks on heterogeneous system, since these algorithms have proven to be very efficient in solving complex computational problems.
-\emph{Genetic algorithms}\cite{article2} can be used to efficiently schedule tasks in different systems.
-Also, \emph{Reinforcement Learning} (RL)\cite{ORHEAN2018292} has been a strong candidate for the problem, as the scheduling problem can be formulated as an \emph{RL} problem, solved by various \emph{RL} techniques.
-Some papers also investigated the usage of \emph{Artificial Neural Networks} (ANN)\cite{article3} in task scheduling in heterogeneous systems. \\ 
-In this paper, we make use of recent advances in \emph{Deep Learning} and build a deep representation of the scheduling problem using \emph{Recurrent Neural Networks}(RNNs)\cite{chung2014empirical} and other techniques.
-
-\section{Methodology}
-
-\subsection{Formulation}
-First, let us specify the main target of this work.
-As the task scheduling in heterogeneous distributed system is a vast field with lots of settings and algorithms\cite{inbook}, we choose our scheduling setting to be local and static.
-The goal of this work is to explore the ability of neural networks to approximate the performance of some well-established scheduling algorithms.
-In our setting, the algorithms are provided a list of tasks, each has its own execution time on different machines and a set of heterogeneous machines, on which the tasks are executed.
-We compare the results neural networks to some other heuristic and approximate methods.
-\\
-Although, we choose local static scheduling, we assume that the neural approximation methods can work in other settings as well.
-
-\subsection{Baseline}
-Two baseline methods are considered.
-We choose \emph{Heterogeneous Earliest Finish Time} (HEFT)\cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems.
-Also, genetic algorithms\cite{article2} is provided as an approximate baseline.
-
-\subsubsection{Heterogeneous Earliest Time First (HEFT)}
-HEFT\cite{993206} is an old and well-established algorithm for scheduling in heterogeneous systems.
-It has been used as a baseline in research due to its near-optimal results.
-Basically, it chooses some process to run on some machine, if the former has the earliest finish time, with considering the special nature of the heterogeneous system.
-However, HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process.
-
-\subsubsection{Genetic Algorithms}
-Genetic algorithms\cite{article2} have proven to be very efficient in solving some of the hardest optimization problem.
-Previous work on the use of genetic algorithms in task scheduling \cite{article2} is adapted to the heterogeneous setting by adding parameters for execution time of different tasks on different machines.
-\\
-The targeted \emph{fitness function} will be the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
-\begin{equation}
-\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N}
-\end{equation}
-
-\subsection{Neural Networks (Deep Learning)}
-The main novel idea of this work is the use of \emph{neural networks} for the scheduling problem.
-Neural Networks are known to be very good at learning representations and function approximation.
-In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.
-\\
-Previous work tried to use neural networks to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}\cite{article3}.
-However, we try to make use of the recent advances in \emph{Deep Learning} to redefine the scheduling problem and solve it.
-\\
-As mentioned, The provided input is a list of tasks with its information and a set of machines.
-We want the network to learn an implicit representation of the given tasks and machines.
-Then, the network learn the mapping between the learned representation and the desired schedule.
-In other words, the target of the network is to take two input list of information of both tasks and machines and then output for each task, the machine to be executed on, the actual start time and the actual finish time.
-
-\subsubsection{Architecture}
-Our architecture consists of two encoders and one decoder, as shown in Fig.\ref{fig:nn}. \\
-The first encoder is a fully convolutional network of \emph{1D} convolutional layers, to which is machines specifications are passed.
-This encoder learns a representation for the machines to be able to use it later in producing the outputs.
-\\
-The second encoder is an \emph{Recurrent Neural Network} (RNN)\cite{chung2014empirical}, to which the tasks are passed one by one ordered by the arrival time.
-This network learns a representation of the tasks preserving the arrival order.
-RNN is chosen due to its proven effectiveness in dealing with sequential data.
-\\
-The two representations are then stacked and passed to two modules.
-A classification module which states the machine on which a specific task is executed.
-A regression module that identifies the actual start time and the actual finish time.
-Mainly, the two modules consist of \emph{1D} convolutional layers.
-
-\begin{figure}[hp]
-    \centering
-    \includegraphics[width=0.45\textwidth]{sched_nn}
-    \caption{The architecture of the proposed neural network for distributed heterogeneous systems scheduling}
-    \label{fig:nn}
-\end{figure}
-
-\subsubsection{Objective Function}
-The cost function defined for this architecture is a sum of two criteria.
-Categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$.
-So it can be summarized as follows:
-\begin{equation}
-\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t)
-\end{equation}
-where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range.
-
-\subsubsection{Downsides}
-The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network.
-These numbers are used to define the network and loss function dimensions.
-
-\section{Experimental Setup}
-
-\section{Discussion and Results}
-
-\section{Conclusion}
-
-\medskip
-
-\bibliographystyle{unsrt}
-\bibliography{paper}
-
-\end{document}

### 2020-04-09 paper/core/methodology.tex
section split into files

--- 2020-04-09 paper/paper.tex
@@
-\documentclass[twocolumn,11pt]{IEEEtran}
-\usepackage[verbose,expansion=alltext,stretch=50]{microtype}
-\usepackage{graphicx}
-
-\title{DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems}
-
-\author{
-   \begin{tabular}{c| c| c| c}
-       Mohamed Shawky & Remonda Talaat & Mahmoud Adas & Evram Youssef\\
-       \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}} & \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}}
-   \end{tabular}%
-
-   \texttt{\small{\{mohamedshawky911, remondatalaat21, mido3ds, evramyousef\}@gmail.com}}
-}%
-
-\markboth{Cairo Uni. CMP Dep. $|$ OS Research $|$ Final Paper $|$ \today}{Shell}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-To be conducted, once the results are complete.  
-\end{abstract}
-
-\section{Introduction}
-
-\IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) have driven our needs for better resource allocation methods.
-The performance of any system critically depends on the algorithms used to schedule tasks on its resources.
-These systems contain limited resources, that should be allocated properly, in order to perform the required tasks with maximum efficiency avoiding starvation and resource exhaustion.
-The general objective of any scheduling technique is to get the best possible performance with a reasonable resource utilization. \\
-
-Recently, the heterogeneity of the computational systems has increased tremendously, due to the nature of the applications and the great advances in IoT and distributed systems.
-A \emph{heterogeneous system} can be defined as a range of resources, different in underlying architecture, targeting different types of computational tasks.
-The usage of a heterogeneous system has proven to be very efficient in increasing the system performance and reducing the overall power consumption.
-Recent studies \cite{venkat2014harnessing} show that \emph{heterogeneous system} can outperform the best homogeneous systems by as much as 21\%, with 23\% energy savings and
-a reduction of 32\% in Energy Delay Product. These numbers can be improved even more with better task scheduling and resource allocation methods. \\
-
-However, this comes with the problem of complex task scheduling.
-The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system, because of the different execution rates of processors and different communication rates among different processors, which add extra layers of complexity to the problem.
-\\
-
-The parameters of such problem make it very suitable for various optimization techniques.
-Recursive optimization techniques are very efficient in solving many optimization problem.
-Previous work has investigated the usage of techniques such as \emph{genetic algorithms} \cite{article2} to solve the task scheduling problem.
-Also, the usage of a progressive decision making techniques such as \emph{Reinforcement Learning} \cite{ORHEAN2018292} for task scheduling in heterogeneous systems has been investigated.
-\\
-
-In this paper, we investigate the ability of advanced predictive models to learn a representation of static local task scheduling problem.
-This learned representation will be used to approximate the scheduling performance of other scheduling techniques.
-\emph{Neural Networks} are our best candidate for this task.
-Neural networks are being used in many fields replacing traditional methods, such as image classification \cite{10.1145/3065386}, object detection \cite{ren2015faster}, neural language modelling \cite{ren2015faster}, image generation \cite{karras2019analyzing} and others.
-They have proven to be more efficient than other traditional methods.
-The complexity of the neural networks comes in the development phases, where the network is designed and trained.
-However, in inference phase, neural networks can achieve very accurate results at high speed.
-Recent work has been done on optimizing neural network inference through various techniques, such as quantization \cite{choukroun2019lowbit} and pruning \cite{yeom2019pruning}.
-\\
-
-The recent advances in \emph{Deep Learning} research is considered in designing and training our scheduling network.
-\emph{Heterogeneous Earliest Time First} (HEFT) \cite{993206} is used as a target, where the network learns to approximate its performance.
-Also, we include a genetic algorithm experiment for the same problem for comparison.
-We will discuss our approach to the problem and its limitations.
-
-\section{Related Work}
-
-Since task scheduling in heterogeneous systems is a wide problem, a lot of research has been conducted in this area.
-Various techniques have been introduced for the problem.
-These techniques are categorized based on multiple aspects \cite{inbook} and some of which are adapted from task scheduling methods for homogeneous systems.
-
-\subsection{Scheduling Categories}
-In this work, we focus on three basic categorization of heterogeneous task scheduling methods.
-
-\subsubsection{Application-Specific vs. System-Specific}
-Heterogeneous scheduling methods can be divided into two main categories based on their target metric.\\
-\emph{Application-Specific} scheduling targets task execution speed (performance), where scheduling
-decisions are determined based on many parameters including application performance, task inter-dependency and the availability of resources.
-\emph{System-Specific} targets resource utilization, where scheduling decisions are based on the percentage of time a resource is available or busy.
-
-\subsubsection{Global vs. Local}
-Also, heterogeneous scheduling methods can be divided into global and local scheduling.
-\emph{Global} scheduling can migrate the tasks from one processor to another, meanwhile \emph{local} scheduling can't migrate, so once a task is assigned to a processor, it stays in its queue.
-
-\subsubsection{Static vs. Dynamic}
-Finally, heterogeneous scheduling methods can be divided into static and dynamic scheduling.
-In \emph{static} scheduling, the tasks required to be scheduled are defined before scheduling.
-However, in \emph{dynamic} scheduling, new tasks can be introduced during the scheduling process
-
-\subsection{Heterogeneous Earliest Time First (HEFT)}
-HEFT \cite{993206} is one of the most well-established algorithms for task scheduling in heterogeneous systems.
-It's a local static scheduling algorithms, which deals with a \emph{Direct Acyclic Graph} (DAG) of tasks displaying the dependencies between different processes.
-Each task has a running time for each different machine and a time for communicating the results to children tasks.
-A wide range of algorithms \cite{inbook} follows HEFT further improving the scheduling performance.
-
-\subsection{Optimization Algorithms}
-Recent research has been conducted to use optimization algorithms and predictive models to schedule tasks on heterogeneous system, since these algorithms have proven to be very efficient in solving complex computational problems.
-\subsubsection{Genetic Algorithms (GA)}
-GA \cite{article2} can be used to efficiently schedule tasks in different systems.
-It's used for static scheduling, where a fixed population of tasks are scheduled recursively on multiple processors, based on a specific fitness function.
-\subsubsection{Reinforcement Learning (RL)}
-Also, RL \cite{ORHEAN2018292} has been a strong candidate for the problem, as the scheduling problem can be formulated as an \emph{RL} problem, solved by various \emph{RL} techniques.
-RL techniques are effective in solving progressive decision making problems, so they are more likely to be used in dynamic scheduling.
-
-\subsection{Neural Networks}
-Recent advances in \emph{Deep Learning} have enabled neural networks to dominate many fields, such as computer vision, natural language processing and others.
-Neural networks are able to perform perception tasks at a human-level accuracy.
-Also, neural networks are very efficient in function approximation and representation learning.
-These properties make neural networks a perfect choice for massive scale automation of many tasks.
-Some studies even investigated the usage of \emph{Artificial Neural Networks} (ANN)\cite{article3} in task scheduling in heterogeneous systems.
-Most of these studies focus on the usage of \emph{Hopfield Nets} \cite{sathasivam2008logic} and \emph{Inhibitor Neurons} \cite{article3}.
-\\
-
-In this paper, we make use of recent advances in \emph{Deep Learning} and build a deep representation of the scheduling problem and use it to approximate the performance of heterogeneous scheduling methods.
-\emph{Recurrent Neural Networks}(RNNs) \cite{chung2014empirical} are used for this purpose, as they have the ability to learn complex temporal information from a time-series data, which is exactly our case.
-Other network operations to be used, too.
-
-\section{Methodology}
-
 \subsection{Motivation}
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{sched_nn}
+    \includegraphics[width=0.45\textwidth]{diagrams/sched_nn}
     \caption{The architecture of the proposed neural network for distributed heterogeneous systems scheduling}
@@
 These numbers are used to define the network and loss function dimensions.
-
-\section{Experimental Setup}
-
-\section{Discussion and Results}
-
-\section{Conclusion}
-
-\medskip
-
-\bibliographystyle{unsrt}
-\bibliography{paper}
-
-\end{document}

### 2020-04-09 paper/core/related_work.tex
section split into files

--- 2020-04-09 paper/paper.tex
@@
-\documentclass[twocolumn,11pt]{IEEEtran}
-\usepackage[verbose,expansion=alltext,stretch=50]{microtype}
-\usepackage{graphicx}
-
-\title{DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems}
-
-\author{
-   \begin{tabular}{c| c| c| c}
-       Mohamed Shawky & Remonda Talaat & Mahmoud Adas & Evram Youssef\\
-       \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}} & \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}}
-   \end{tabular}%
-
-   \texttt{\small{\{mohamedshawky911, remondatalaat21, mido3ds, evramyousef\}@gmail.com}}
-}%
-
-\markboth{Cairo Uni. CMP Dep. $|$ OS Research $|$ Final Paper $|$ \today}{Shell}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-To be conducted, once the results are complete.  
-\end{abstract}
-
-\section{Introduction}
-
-\IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) have driven our needs for better resource allocation methods.
-The performance of any system critically depends on the algorithms used to schedule tasks on its resources.
-These systems contain limited resources, that should be allocated properly, in order to perform the required tasks with maximum efficiency avoiding starvation and resource exhaustion.
-The general objective of any scheduling technique is to get the best possible performance with a reasonable resource utilization. \\
-
-Recently, the heterogeneity of the computational systems has increased tremendously, due to the nature of the applications and the great advances in IoT and distributed systems.
-A \emph{heterogeneous system} can be defined as a range of resources, different in underlying architecture, targeting different types of computational tasks.
-The usage of a heterogeneous system has proven to be very efficient in increasing the system performance and reducing the overall power consumption.
-Recent studies \cite{venkat2014harnessing} show that \emph{heterogeneous system} can outperform the best homogeneous systems by as much as 21\%, with 23\% energy savings and
-a reduction of 32\% in Energy Delay Product. These numbers can be improved even more with better task scheduling and resource allocation methods. \\
-
-However, this comes with the problem of complex task scheduling.
-The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system, because of the different execution rates of processors and different communication rates among different processors, which add extra layers of complexity to the problem.
-\\
-
-The parameters of such problem make it very suitable for various optimization techniques.
-Recursive optimization techniques are very efficient in solving many optimization problem.
-Previous work has investigated the usage of techniques such as \emph{genetic algorithms} \cite{article2} to solve the task scheduling problem.
-Also, the usage of a progressive decision making techniques such as \emph{Reinforcement Learning} \cite{ORHEAN2018292} for task scheduling in heterogeneous systems has been investigated.
-\\
-
-In this paper, we investigate the ability of advanced predictive models to learn a representation of static local task scheduling problem.
-This learned representation will be used to approximate the scheduling performance of other scheduling techniques.
-\emph{Neural Networks} are our best candidate for this task.
-Neural networks are being used in many fields replacing traditional methods, such as image classification \cite{10.1145/3065386}, object detection \cite{ren2015faster}, neural language modelling \cite{ren2015faster}, image generation \cite{karras2019analyzing} and others.
-They have proven to be more efficient than other traditional methods.
-The complexity of the neural networks comes in the development phases, where the network is designed and trained.
-However, in inference phase, neural networks can achieve very accurate results at high speed.
-Recent work has been done on optimizing neural network inference through various techniques, such as quantization \cite{choukroun2019lowbit} and pruning \cite{yeom2019pruning}.
-\\
-
-The recent advances in \emph{Deep Learning} research is considered in designing and training our scheduling network.
-\emph{Heterogeneous Earliest Time First} (HEFT) \cite{993206} is used as a target, where the network learns to approximate its performance.
-Also, we include a genetic algorithm experiment for the same problem for comparison.
-We will discuss our approach to the problem and its limitations.
-
-\section{Related Work}
-
 Since task scheduling in heterogeneous systems is a wide problem, a lot of research has been conducted in this area.
@@
 Other network operations to be used, too.
-
-\section{Methodology}
-
-\subsection{Formulation}
-First, let us specify the main target of this work.
-As the task scheduling in heterogeneous distributed system is a vast field with lots of settings and algorithms\cite{inbook}, we choose our scheduling setting to be local and static.
-The goal of this work is to explore the ability of neural networks to approximate the performance of some well-established scheduling algorithms.
-In our setting, the algorithms are provided a list of tasks, each has its own execution time on different machines and a set of heterogeneous machines, on which the tasks are executed.
-We compare the results neural networks to some other heuristic and approximate methods.
-\\
-Although, we choose local static scheduling, we assume that the neural approximation methods can work in other settings as well.
-
-\subsection{Baseline}
-Two baseline methods are considered.
-We choose \emph{Heterogeneous Earliest Finish Time} (HEFT)\cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems.
-Also, genetic algorithms\cite{article2} is provided as an approximate baseline.
-
-\subsubsection{Heterogeneous Earliest Time First (HEFT)}
-HEFT\cite{993206} is an old and well-established algorithm for scheduling in heterogeneous systems.
-It has been used as a baseline in research due to its near-optimal results.
-Basically, it chooses some process to run on some machine, if the former has the earliest finish time, with considering the special nature of the heterogeneous system.
-However, HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process.
-
-\subsubsection{Genetic Algorithms}
-Genetic algorithms\cite{article2} have proven to be very efficient in solving some of the hardest optimization problem.
-Previous work on the use of genetic algorithms in task scheduling \cite{article2} is adapted to the heterogeneous setting by adding parameters for execution time of different tasks on different machines.
-\\
-The targeted \emph{fitness function} will be the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
-\begin{equation}
-\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N}
-\end{equation}
-
-\subsection{Neural Networks (Deep Learning)}
-The main novel idea of this work is the use of \emph{neural networks} for the scheduling problem.
-Neural Networks are known to be very good at learning representations and function approximation.
-In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.
-\\
-Previous work tried to use neural networks to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}\cite{article3}.
-However, we try to make use of the recent advances in \emph{Deep Learning} to redefine the scheduling problem and solve it.
-\\
-As mentioned, The provided input is a list of tasks with its information and a set of machines.
-We want the network to learn an implicit representation of the given tasks and machines.
-Then, the network learn the mapping between the learned representation and the desired schedule.
-In other words, the target of the network is to take two input list of information of both tasks and machines and then output for each task, the machine to be executed on, the actual start time and the actual finish time.
-
-\subsubsection{Architecture}
-Our architecture consists of two encoders and one decoder, as shown in Fig.\ref{fig:nn}. \\
-The first encoder is a fully convolutional network of \emph{1D} convolutional layers, to which is machines specifications are passed.
-This encoder learns a representation for the machines to be able to use it later in producing the outputs.
-\\
-The second encoder is an \emph{Recurrent Neural Network} (RNN)\cite{chung2014empirical}, to which the tasks are passed one by one ordered by the arrival time.
-This network learns a representation of the tasks preserving the arrival order.
-RNN is chosen due to its proven effectiveness in dealing with sequential data.
-\\
-The two representations are then stacked and passed to two modules.
-A classification module which states the machine on which a specific task is executed.
-A regression module that identifies the actual start time and the actual finish time.
-Mainly, the two modules consist of \emph{1D} convolutional layers.
-
-\begin{figure}[hp]
-    \centering
-    \includegraphics[width=0.45\textwidth]{sched_nn}
-    \caption{The architecture of the proposed neural network for distributed heterogeneous systems scheduling}
-    \label{fig:nn}
-\end{figure}
-
-\subsubsection{Objective Function}
-The cost function defined for this architecture is a sum of two criteria.
-Categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$.
-So it can be summarized as follows:
-\begin{equation}
-\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t)
-\end{equation}
-where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range.
-
-\subsubsection{Downsides}
-The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network.
-These numbers are used to define the network and loss function dimensions.
-
-\section{Experimental Setup}
-
-\section{Discussion and Results}
-
-\section{Conclusion}
-
-\medskip
-
-\bibliographystyle{unsrt}
-\bibliography{paper}
-
-\end{document}

### 2020-04-09 paper/paper.tex
section split into files

--- 2020-04-09 paper/paper.tex
@@
 \begin{abstract}
-To be conducted, once the results are complete.  
+
 \end{abstract}
@@
 \section{Introduction}
-
-\IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) have driven our needs for better resource allocation methods.
-The performance of any system critically depends on the algorithms used to schedule tasks on its resources.
-These systems contain limited resources, that should be allocated properly, in order to perform the required tasks with maximum efficiency avoiding starvation and resource exhaustion.
-The general objective of any scheduling technique is to get the best possible performance with a reasonable resource utilization. \\
-
-Recently, the heterogeneity of the computational systems has increased tremendously, due to the nature of the applications and the great advances in IoT and distributed systems.
-A \emph{heterogeneous system} can be defined as a range of resources, different in underlying architecture, targeting different types of computational tasks.
-The usage of a heterogeneous system has proven to be very efficient in increasing the system performance and reducing the overall power consumption.
-Recent studies \cite{venkat2014harnessing} show that \emph{heterogeneous system} can outperform the best homogeneous systems by as much as 21\%, with 23\% energy savings and
-a reduction of 32\% in Energy Delay Product. These numbers can be improved even more with better task scheduling and resource allocation methods. \\
-
-However, this comes with the problem of complex task scheduling.
-The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system, because of the different execution rates of processors and different communication rates among different processors, which add extra layers of complexity to the problem.
-\\
-
-The parameters of such problem make it very suitable for various optimization techniques.
-Recursive optimization techniques are very efficient in solving many optimization problem.
-Previous work has investigated the usage of techniques such as \emph{genetic algorithms} \cite{article2} to solve the task scheduling problem.
-Also, the usage of a progressive decision making techniques such as \emph{Reinforcement Learning} \cite{ORHEAN2018292} for task scheduling in heterogeneous systems has been investigated.
-\\
-
-In this paper, we investigate the ability of advanced predictive models to learn a representation of static local task scheduling problem.
-This learned representation will be used to approximate the scheduling performance of other scheduling techniques.
-\emph{Neural Networks} are our best candidate for this task.
-Neural networks are being used in many fields replacing traditional methods, such as image classification \cite{10.1145/3065386}, object detection \cite{ren2015faster}, neural language modelling \cite{ren2015faster}, image generation \cite{karras2019analyzing} and others.
-They have proven to be more efficient than other traditional methods.
-The complexity of the neural networks comes in the development phases, where the network is designed and trained.
-However, in inference phase, neural networks can achieve very accurate results at high speed.
-Recent work has been done on optimizing neural network inference through various techniques, such as  \cite{choukroun2019lowbit} and pruning \cite{yeom2019pruning}.
-\\
-
-The recent advances in \emph{Deep Learning} research is considered in designing and training our scheduling network.
-\emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is used as a target, where the network learns to approximate its performance.
-Also, we include a genetic algorithm experiment for the same problem for comparison.
-We will discuss our approach to the problem and its limitations.
+\input{core/introduction}
 
 \section{Related Work}
-
-Since task scheduling in heterogeneous systems is a wide problem, a lot of research has been conducted in this area. Various techniques have been introduced for the problem. 
-The scheduling algorithms for heterogeneous distributed systems are divided into two main categories based on their target metric.
-Application-Specific scheduling targets job execution speed (performance).
-System-Specific targets resource utilization.
-\\
-\emph{Heterogeneous Earliest Time First} (HEFT)\cite{993206} is one of the most well-established algorithms for task scheduling in heterogeneous systems. 
-It's a local static scheduling algorithms, which deals with a \emph{Direct Acyclic Graph} (DAG) of tasks displaying the dependencies between different processes.
-Each task has a running time for each different machine and a time for communicating the results to children tasks.
-A wide range of algorithms\cite{inbook} follows HEFT further improving the scheduling performance. \\
-Recent research has been conducted to use optimization algorithms and predictive models to schedule tasks on heterogeneous system, since these algorithms have proven to be very efficient in solving complex computational problems.
-\emph{Genetic algorithms}\cite{article2} can be used to efficiently schedule tasks in different systems.
-Also, \emph{Reinforcement Learning} (RL)\cite{ORHEAN2018292} has been a strong candidate for the problem, as the scheduling problem can be formulated as an \emph{RL} problem, solved by various \emph{RL} techniques.
-Some papers also investigated the usage of \emph{Artificial Neural Networks} (ANN)\cite{article3} in task scheduling in heterogeneous systems. \\ 
-In this paper, we make use of recent advances in \emph{Deep Learning} and build a deep representation of the scheduling problem using \emph{Recurrent Neural Networks}(RNNs)\cite{chung2014empirical} and other techniques.
+\input{core/related_work}
 
 \section{Methodology}
-
-\subsection{Formulation}
-First, let us specify the main target of this work.
-As the task scheduling in heterogeneous distributed system is a vast field with lots of settings and algorithms\cite{inbook}, we choose our scheduling setting to be local and static.
-The goal of this work is to explore the ability of neural networks to approximate the performance of some well-established scheduling algorithms.
-In our setting, the algorithms are provided a list of tasks, each has its own execution time on different machines and a set of heterogeneous machines, on which the tasks are executed.
-We compare the results neural networks to some other heuristic and approximate methods.
-\\
-Although, we choose local static scheduling, we assume that the neural approximation methods can work in other settings as well.
-
-\subsection{Baseline}
-Two baseline methods are considered.
-We choose \emph{Heterogeneous Earliest Finish Time} (HEFT)\cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems.
-Also, genetic algorithms\cite{article2} is provided as an approximate baseline.
-
-\subsubsection{Heterogeneous Earliest Time First (HEFT)}
-HEFT\cite{993206} is an old and well-established algorithm for scheduling in heterogeneous systems.
-It has been used as a baseline in research due to its near-optimal results.
-Basically, it chooses some process to run on some machine, if the former has the earliest finish time, with considering the special nature of the heterogeneous system.
-However, HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process.
-
-\subsubsection{Genetic Algorithms}
-Genetic algorithms\cite{article2} have proven to be very efficient in solving some of the hardest optimization problem.
-Previous work on the use of genetic algorithms in task scheduling \cite{article2} is adapted to the heterogeneous setting by adding parameters for execution time of different tasks on different machines.
-\\
-The targeted \emph{fitness function} will be the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
-\begin{equation}
-\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N}
-\end{equation}
-
-\subsection{Neural Networks (Deep Learning)}
-The main novel idea of this work is the use of \emph{neural networks} for the scheduling problem.
-Neural Networks are known to be very good at learning representations and function approximation.
-In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem.
-\\
-Previous work tried to use neural networks to solve scheduling problem through \emph{Hopfield Nets} and \emph{Inhibitor Neurons}\cite{article3}.
-However, we try to make use of the recent advances in \emph{Deep Learning} to redefine the scheduling problem and solve it.
-\\
-As mentioned, The provided input is a list of tasks with its information and a set of machines.
-We want the network to learn an implicit representation of the given tasks and machines.
-Then, the network learn the mapping between the learned representation and the desired schedule.
-In other words, the target of the network is to take two input list of information of both tasks and machines and then output for each task, the machine to be executed on, the actual start time and the actual finish time.
-
-\subsubsection{Architecture}
-Our architecture consists of two encoders and one decoder, as shown in Fig.\ref{fig:nn}. \\
-The first encoder is a fully convolutional network of \emph{1D} convolutional layers, to which is machines specifications are passed.
-This encoder learns a representation for the machines to be able to use it later in producing the outputs.
-\\
-The second encoder is an \emph{Recurrent Neural Network} (RNN)\cite{chung2014empirical}, to which the tasks are passed one by one ordered by the arrival time.
-This network learns a representation of the tasks preserving the arrival order.
-RNN is chosen due to its proven effectiveness in dealing with sequential data.
-\\
-The two representations are then stacked and passed to two modules.
-A classification module which states the machine on which a specific task is executed.
-A regression module that identifies the actual start time and the actual finish time.
-Mainly, the two modules consist of \emph{1D} convolutional layers.
-
-\begin{figure}[hp]
-    \centering
-    \includegraphics[width=0.45\textwidth]{sched_nn}
-    \caption{The architecture of the proposed neural network for distributed heterogeneous systems scheduling}
-    \label{fig:nn}
-\end{figure}
-
-\subsubsection{Objective Function}
-The cost function defined for this architecture is a sum of two criteria.
-Categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$.
-So it can be summarized as follows:
-\begin{equation}
-\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t)
-\end{equation}
-where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range.
-
-\subsubsection{Downsides}
-The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network.
-These numbers are used to define the network and loss function dimensions.
+\input{core/methodology}
 
 \section{Experimental Setup}
+\input{core/exp_setup}
 
 \section{Discussion and Results}
+\input{core/results}
 
 \section{Conclusion}
+\input{core/conclusion}
 

### 2020-04-09 paper/core/exp_setup.tex
added experimental setup section

\begin{figure}[hp]
    \centering
    \includegraphics[width=0.45\textwidth]{diagrams/framework}
    \caption{The training framework of DeepSched network. A database of tasks and resources is provided for both network and HEFT. The loss of the network is measured based on HEFT produced schedule.}
    \label{fig:fw}
\end{figure}

Our evaluation methodology of the proposed network is based on comparison with two basic method. One of them is a heuristic method, which is \emph{Heterogeneous Earliest Time First} (HEFT) and the other is an approximate method, which is \emph{Genetic Algorithms} (GA). \\

The results are compared based on the execution time, as well as scheduling performance. For execution time, we measure the total time consumed by scheduling different number of tasks. For scheduling performance, we measure the total turnaround time for all scheduled tasks. Our network is supposed to achieve better execution time with similar performance to HEFT on previously seen data and slightly lower performance on unseen data.

\subsection{Baseline}
HEFT, which is a heuristic method, is used as a comparison baseline and also to generate the training data, where the network approximates HEFT performance. GA solution, which is an approximate method, is only used as a comparison baseline. \\

\subsubsection{HEFT}
The basic architecture from the original paper \cite{993206} is used in a framework with the proposed neural network shown in Fig.\ref{fig:fw}. HEFT receives some data from a defined database of tasks and resources and produces the output schedule, which is used as labels for the network training data. This way the network can approximate the performance of the HEFT scheduling algorithm by learning to map the input tasks and resources to the schedule produced by HEFT on a large database. \\

\subsubsection{Genetic Algorithms}
The methodology from \cite{article2} is used to develop a genetic algorithm solution for heterogeneous systems. Extra parameters are added to the population to represent the different resources. Also, the execution time is expanded to be a value for each job running on a specific machine, instead of only one execution time value. The used fitness function is the average waiting time \ref{eq:ga}. Random initialization is used along with Crossover. The results of this method are compared to the output of the proposed network.

\subsection{Datasets}
A database of tasks and resources is adapted from \emph{Dataset for Task scheduling in Cloud using CLoudsim} \cite{px5b-b729-20}. The used database consists of $100000$ training samples represented as a list of tasks requires to be scheduled. Each training sample contains from $486$ to $84654$ tasks, arranged as a \emph{directed acyclic graph} (DAG) to represent the task dependencies and each task has an execution time for each specific processor. Also, the database contains $188$ resource instances (processors), on which the given tasks scheduled. The desired output of such data is to determine, for each task, the optimal processor to run on, the actual start time (AST) and the actual finish time (AFT).

\subsection{Implementation Details}
Our proposed network consists of four main modules.

\subsubsection{Machine Encoder}
This module takes resource details as an input and learns a meaningful representation of them. It consists of one \emph{Conv1D} layer to extract the basic features of each processor, followed by one \emph{fully connected} layer to learn a compact representation of all processors, in order to be passed to the output modules. The common input features for each processor passed to this module are number of processor cores, core frequency and memory capacity. \\

\subsubsection{Task Encoder}
This module takes the time sequence of tasks required to be scheduled and learns a meaningful representation of them through time. \emph{Recurrent neural networks} are used to learn the desired temporal information of the tasks. The module consists of a single \emph{bidirectional gated recurrent unit} (GRU) \cite{chung2014empirical} layer to extract temporal features of each task, followed by one \emph{fully connected} layer to learn a compact representation of all tasks, in order to be passed to the output modules. The common input features for each task passed to this module are arrival time, burst (execution) time for each processor, task priority and memory utilization. \\

The outputs of the previous stages are fused with each other by stacking, in order to form one chunk of information, which is then passed to the two output modules. \\

\subsubsection{Classifier}
The target of this module is to select the optimal running processor for each task amongst the given set of processors. The input to this module is the stacked information of both resources and tasks. It consists of a single \emph{Conv1D} layer, which is used to select running processor for each single task in the form of one hot encoding of the length of resources number. \\

\subsubsection{Regressor}
The target of this module is to predict the actual start time and the actual finish time of each task on the scheduled processor. The input to this module is the stacked information of both resources and tasks. It consists of a single \emph{Conv1D} layer, which is used to regress the actual start and finish times for each task.

\subsection{Training}
The network is trained on HEFT scheduling outputs. Cross-entropy is used as a classification loss and mean squared error (MSE) is used as a regression loss. The summation of the two losses \ref{eq:l} is used to train the network using gradient descent with \emph{Adam} optimizer and a learning rate of $1e$-$5$. The network is trained for $100$ epochs. The training takes around $1.5$ hours on \emph{Nvidia GTX} $1070$ and around $13$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance.

\subsection{Inference}
Inference is performed on the trained network using both seen and unseen data, in order to compare with both HEFT and genetic algorithms, based on time and performance.

### 2020-04-09 paper/core/methodology.tex
added experimental setup section

@@
 
-The targeted \emph{fitness function} will be the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
+The targeted \emph{fitness function} is the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
 \begin{equation}
-\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N}
+\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N} \label{eq:ga}
 \end{equation}
@@
 
+\begin{figure}[hp]
+    \centering
+    \includegraphics[width=0.45\textwidth]{diagrams/sched_nn}
+    \caption{The architecture of the proposed neural network (DeepSched) for distributed heterogeneous systems scheduling.}
+    \label{fig:nn}
+\end{figure}
+
 \subsubsection{Architecture}
@@
 
-\begin{figure}[hp]
-    \centering
-    \includegraphics[width=0.45\textwidth]{diagrams/sched_nn}
-    \caption{The architecture of the proposed neural network for distributed heterogeneous systems scheduling}
-    \label{fig:nn}
-\end{figure}
-
 \subsubsection{Objective Function}
@@
 \begin{equation}
-\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t)
+\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t) \label{eq:l}
 \end{equation}

### 2020-04-10 development/heft_scheduler/main.c
added HEFT scheduler code

@@ -1,0 +1,354 @@
+/*******************************************************
+	    HEFT DUPLICATION IMPLEMENTATION
+********************************************************/
+//NOTES
+//UPPER RANK ARRAY(tasks_upper_rank[]) INITIALIZED TO -1 SO AS TO PREVENT REDUNDANT CALCULATION OF UPPER RANKS
+//COMMUNICATION COST MATRIX(data[][]) HAS -1 VALUE FOR NON COMMUNICATING TASKS
+
+
+#include<stdio.h>
+#include<stdlib.h>
+int no_tasks,no_machines;
+double **computation_costs,**data_transfer_rate,**data,*tasks_upper_rank;
+int *sorted_tasks;
+
+struct TaskProcessor
+{
+    int processor;
+    double AST;
+    double AFT;
+};
+
+struct TaskProcessor *schedule;
+/*******************************************************
+	FUNCTION FOR DETERMINATION OF UPPER RANK
+********************************************************/
+// Calculate average communication cost and give feed to sorted task array
+void insertinto(int task,double rank)
+{
+    static int pos;
+    int i;
+    for(i=pos-1; i>=0; i--)
+        if(rank>tasks_upper_rank[sorted_tasks[i]])
+            sorted_tasks[i+1]=sorted_tasks[i];
+        else
+            break;
+    sorted_tasks[i+1]=task;
+    pos++;
+}
+
+// Calculate the average cost of communication between source and destination
+double avg_communicationcost(int source,int destination)
+{
+    int i,j;
+    double avg=0.0;
+    for(i=0; i<no_machines; i++)
+        for(j=0; j<no_machines; j++)
+        {
+            if(data_transfer_rate[i][j]!=0)
+                avg+=(data[source][destination]/data_transfer_rate[i][j]);
+        }
+    avg=avg/(no_machines*no_machines-no_machines);
+    return avg;
+}
+
+// Calculate the upper rank
+double calculate_upper_rank(int task)
+{
+    int j;
+    double avg_communication_cost,successor,avg=0.0,max=0,rank_successor;
+
+    for(j=0; j<no_machines; j++)
+        avg+=computation_costs[task][j];
+    avg/=no_machines;
+
+    for(j=0; j<no_tasks; j++)
+    {
+        // Check if node(j) is a successor of node(task)
+        if(data[task][j]!=-1)
+        {
+            avg_communication_cost=avg_communicationcost(task,j);
[…]

### 2020-04-10 paper/core/exp_setup.tex
added train/test split note to setup section

@@
 A database of tasks and resources is adapted from \emph{Dataset for Task scheduling in Cloud using CLoudsim} \cite{px5b-b729-20}.
-The used database consists of $100000$ training samples represented as a list of tasks requires to be scheduled.
-Each training sample contains from $486$ to $84654$ tasks, arranged as a \emph{directed acyclic graph} (DAG) to represent the task dependencies and each task has an execution time for each specific processor.
+The used database consists of $100000$ samples represented as a list of tasks requires to be scheduled.
+Each sample contains from $486$ to $84654$ tasks, arranged as a \emph{directed acyclic graph} (DAG) to represent the task dependencies and each task has an execution time for each specific processor.
 Also, the database contains $188$ resource instances (processors), on which the given tasks scheduled.
 The desired output of such data is to determine, for each task, the optimal processor to run on, the actual start time (AST) and the actual finish time (AFT).
+
+The provided samples are divided into $90000$ samples for training and validation and $10000$  samples for testing.
+We maintain diversity in the test data by including different number of tasks in the test samples.
 

### 2020-04-10 development/nn_scheduler/inference.py
trainer/inference timer

@@ -2,10 +2,12 @@ from data_loader.dataloader import SchedDataset
 from model import SchedNN
 import torch.nn as nn
 from torch.utils.data import DataLoader
+from timeit import default_timer
 import numpy as np
 import argparse
 import torch
 import math
+import os
 
 def main(args=None):
     parser = argparse.ArgumentParser(description=__doc__)
@@ -17,6 +19,9 @@ def main(args=None):
     parser.add_argument('--batch_size', help='Batch size.', type=int, default=8)
 
     args = parser.parse_args(args)
+
+    if (os.path.isdir("data/outputs/")):
+        os.mkdir("data/outputs/")
     
     device = "cuda:0" if torch.cuda.is_available else "cpu"
 
@@ -31,6 +36,9 @@ def main(args=None):
     steps_num = int(math.ceil(len(dataset)/ args.batch_size))
 
     print("The model contains: {} parameters".format(sum(p.numel() for p in model.parameters())))
+    print("Inference on {} samples".format(len(dataset)))
+
+    start_time = default_timer()
 
     for step in range(steps_num):
         X_machine, X_job, Y_machine, Y_time = next(data_iterator)
@@ -40,6 +48,8 @@ def main(args=None):
         print("Saving output #{} ...".format(step))
         np.save("data/outputs/{}_machines.npy".format(step), out_machine.cpu().detach().numpy())
         np.save("data/outputs/{}_times.npy".format(step), out_time.cpu().detach().numpy())
+    
+    print("Inference finished in {}".format(default_timer()-start_time))    
 
 if __name__ == '__main__':
     main()

### 2020-04-10 development/nn_scheduler/trainer.py

@@ -5,6 +5,7 @@ from torch.utils.data import DataLoader
 import argparse
 import torch
 import math
+import os
 
 def main(args=None):
     parser = argparse.ArgumentParser(description=__doc__)
@@ -22,6 +23,9 @@ def main(args=None):
     parser.add_argument('--job_dim', help='Number of features per job.', type=int, default=4)
 
     args = parser.parse_args(args)
+
+    if (os.path.isdir("checkpoints/")):
+        os.mkdir("checkpoints/")
     
     device = "cuda:0" if torch.cuda.is_available else "cpu"
 

### 2020-04-10 paper/core/exp_setup.tex
added evaluation and TA chart

@@
 Extra parameters are added to the population to represent the different resources.
-Also, the execution time is expanded to be a value for each job running on a specific machine, instead of only one execution time value.
+Also, the execution time is expanded to be a value for each task running on a specific machine, instead of only one execution time value.
 The used fitness function is the average waiting time \ref{eq:ga}.
@@
 The desired output of such data is to determine, for each task, the optimal processor to run on, the actual start time (AST) and the actual finish time (AFT).
+\\
 
@@
 The network is trained for $100$ epochs.
-The training takes around $1.5$ hours on \emph{Nvidia GTX} $1070$ and around $13$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance.
+The task encoder only takes input of maximum number of tasks, so inputs of lower dimension are zero-padded along the length dimension to the maximum number ($84654$ tasks).
+\\
+
+The training takes around $1.5$ hours on \emph{Nvidia GTX} $1070$ and around $15$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance.
 
 \subsection{Inference}
-Inference is performed on the trained network using both seen and unseen data, in order to compare with both HEFT and genetic algorithms, based on time and performance.
+Inference is performed on the trained network using both train and test data.
+We use the same $188$ resources information for all tests, however the input list of tasks is zero-padded to the maximum number of tasks, exactly like training.
+
+\subsection{Evaluation}
+The evaluation of our proposed method is conducted through running inference on both seen and unseen data of different lengths.
+These results of the network are compared to the output of HEFT and GA methods in the same scenarios.
+
+This is done by passing the schedule produced by the three methods through a simple simulation that runs the proposed schedule and calculates the average turnaround time of all tasks.
+Evaluation is also conducted on the execution time of each scheduling method, as the speed of the scheduling algorithm is one of our main targets.

### 2020-04-10 paper/core/exp_setup.tex
separate repo for network
added results chart and table

@@
 
-The training takes around $1.5$ hours on \emph{Nvidia GTX} $1070$ and around $15$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance.
+The training takes around $35$ minutes on \emph{Nvidia GTX} $1070$ and around $12$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance. \\
+
+The proposed network is implemented in \emph{Python} using \emph{PyTorch} framework \cite{paszke2019pytorch}.  Our source code is publicly available at \link{https://github.com/DarkGeekMS/deepsched}.
 

### 2020-04-10 paper/core/results.tex
added results chart and table

\subsection{Scheduling Performance}

\begin{figure}[hp]
    \centering
    \includegraphics[width=0.45\textwidth]{diagrams/ta_chart}
    \caption{Average turnaround time produced from the three discussed schedulers at different input sizes.}
    \label{fig:ta_chart}
\end{figure}

\subsection{Execution Time}

\begin{table}
  \caption{Time comparison between the three discussed schedulers at different input sizes. Time measured in seconds.}
  \label{tab:exec_time}
  \centering
  \begin{tabular}{l l l l}
    \toprule
    Input Size & HEFT & GA & NN \\
    \midrule
    486	& 31.5 & 67.5 & 0.125 \\
    10000 & 305.5 & 602.5 & 0.125 \\
    84654 & 670.0 & 3967.0 & 0.125 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Results Discussion}

### 2020-04-11 paper/core/methodology.tex
added discussion and results section

@@
 
-\subsubsection{Downsides}
+\subsubsection{Drawbacks}
 The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network.

### 2020-04-11 paper/core/results.tex
added discussion and results section

@@
 
-\begin{figure}[hp]
-    \centering
-    \includegraphics[width=0.45\textwidth]{diagrams/ta_chart}
-    \caption{Average turnaround time produced from the three discussed schedulers at different input sizes.}
-    \label{fig:ta_chart}
-\end{figure}
+Fig.\ref{fig:ta_chart} shows the scheduling performance of different scheduling methods at different input sizes.
+The proposed network shows almost the same average turnaround time as HEFT algorithm for the seen data during training.
+However, for unseen data, the network shows slightly more poor performance than HEFT, but still better than that of genetic algorithms.
+
+These results refer to the network ability to learn a good representation to the input machines and scheduling problem.
+The network performance degrades with high input sizes, as it's approximating HEFT, which is basically a greedy algorithm and prone to failure at complex situations.
+Genetic algorithms shows similar behaviour too, due to large population size.
 
 \subsection{Execution Time}
-
 \begin{table}
@@
 
+The main advantage of using neural networks is constant inference time.
+Once the network is trained, it takes a static execution time in inference, as it's a simple feedforward process.
+Table \ref{tab:exec_time} shows the execution time of the discussed schedulers at 3 different input sizes.
+These number are produced running on \emph{Intel i5-6600K}.
+
+We can see that the network consumes constant time in inference with different input sizes.
+This is because the network is trained on the maximum input length.
+However, HEFT and genetic algorithms execution time increases with input size.
+GA time increases more rapidly than HEFT, as it's a recursive optimization method but HEFT is a greedy-based method.
+
 \subsection{Results Discussion}
+The previous results show that neural networks can approximate a scheduling algorithm for heterogeneous distributed systems, resulting in a significantly-good performance and fast execution.
+The proposed network can perform well, even on unseen data it can produce efficient schedules.
+
+However, this comes with a drawback of static scenarios.
+The neural network is trained with fixed input size, which is the maximum number of tasks, in our case.
+At inference time, the input to the network can't exceed that number.
+So, we have to define the maximum number of tasks to be scheduled, as well as the maximum number of resources.
+Moreover, the scheduling scenario for the proposed network should be static, where all available tasks should be known before the scheduler starts.
+
+This gives neural networks a great potential to be a good task scheduler in static scenarios, where the maximum number of tasks and resources are known.
+However, in other dynamic scenarios, neural networks might not help much.

### 2020-04-11 paper/paper.tex
added evaluation and TA chart
added results chart and table
added abstract

@@
 \usepackage{graphicx}
+\usepackage{booktabs}
+\usepackage{hyperref}
+\usepackage{xcolor}
+\newcommand{\link}[1]{{\color{blue}\href{#1}{#1}}}
 
@@
 \begin{abstract}
-
+Task scheduling is one of the core problems in any distributed system.
+The ability of the system to assign tasks to its different resources to achieve the best possible performance with the least resource consumption is the main challenge in distributed systems research.
+The heterogeneity of the distributed systems adds another layer of complexity on top of the mentioned problem.
+The different execution time on different processors and different task dependencies make the scheduling problem very computationally intensive.
+Usually, researchers and developers turn to greedy-based methods or even recursive optimization methods to reach some optimal or sub-optimal solution.
+However, due to the nature of the problem, these solutions might take very long time and usually degrade in complex situations.
+In this work, we propose the idea of scheduling algorithms approximation, where we approximate the complex scheduling algorithms using other models to achieve the same results but with lower execution time.
+Neural networks are proposed for this task, as they are great function approximators.
+The complexity of neural networks comes at training time, however they can maintain constant execution time in inference.
+This constant execution time is relatively low, as it's a simple feedforward process.
+This makes neural networks a perfect candidate for us, however this comes at a cost of static scheduling scenarios.
 \end{abstract}
@@
 
+\section{Future Work}
+\input{core/future_work}
+
 \medskip

### 2020-04-12 paper/core/conclusion.tex
conclusion and abstract extension

In this work, we propose a new approximation method of task scheduling algorithms in heterogeneous distributed system using neural networks. The proposed network is used to approximate HEFT scheduler in static scheduling scenarios. The network can perform as accurate as HEFT on seen data during training and sightly lower performance on unseen data. However, the network can maintain a constant execution time at different input sizes, while HEFT execution time increases rapidly.

These results show that neural network, which are great function approximators, have the potential to approximate different scheduling methods for heterogeneous distributed systems. They can learn good representation of the scheduling problem, while maintaining constant execution time in inference.

The main drawback of this method is that static scenarios must be provided. Maximum number to tasks to be scheduled and maximum number of resources must be known before training the network. However, the proposed network is relatively small and doesn't consume much time to train on low or mid-range \emph{GPUs}. \\

In conclusion, It's a trade-off between constant time execution and dynamic systems, where good performance and constant execution time can be achieved in neural networks at static scenarios. This can be useful in some cases such as simulations on supercomputers, where the workflow is static and initially defined. Meanwhile, other solutions, such as RL solutions, can work well in a dynamic environment with no degradation with the complexity of the environment. This is important in IoT-based application, where the system is totally dynamic and can have different events.

### 2020-04-12 paper/paper.tex
conclusion and abstract extension

@@
 This constant execution time is relatively low, as it's a simple feedforward process.
-This makes neural networks a perfect candidate for us, however this comes at a cost of static scheduling scenarios.
+This makes neural networks a perfect candidate for us, however this comes at a cost of static scheduling scenarios, which is useful in some case such as simulation workflow on supercomputers.
+The proposed network can achieve almost the same performance of the approximated method (HEFT) on seen data during training and slightly worse performance on unseen data.
 \end{abstract}

### 2020-04-12 paper/core/conclusion.tex
added future work

@@
+\subsection{Conclusion}
+
 In this work, we propose a new approximation method of task scheduling algorithms in heterogeneous distributed system using neural networks.
@@
 This is important in IoT-based application, where the system is totally dynamic and can have different events.
+
+\subsection{Future Work}
+
+This work can be improved in two possible ways.
+\emph{First,} other heterogeneous task scheduling methods can be approximated using neural networks.
+As we mentioned, the proposed method can be expanded to approximate other scheduling methods as long as static scenarios provided.
+Neural networks can even approximate theoretical methods, that achieves optimal results, to a great extend.
+These methods aren't used in real life due to there time complexity.
+However, if these methods are approximated using neural networks, they can be deployed in real life applications.
+
+\emph{Second,} Other possible approximation methods can be tried through neural networks in order to confront dynamic scenarios.
+Online optimization can be one solution, however online network optimization can be very computationally-expensive.
+Another possible solution is to use the proposed network as a function approximator in a \emph{Reinforcement Learning} (RL) environment, in order to be able to learn dynamically in case of new introduced tasks.

### 2020-04-12 paper/core/results.tex
added abstract
added future work

@@
+\begin{figure}[hp]
+    \centering
+    \includegraphics[width=0.45\textwidth]{diagrams/ta_chart}
+    \caption{Average turnaround time produced from the three discussed schedulers at different input sizes.}
+    \label{fig:ta_chart}
+\end{figure}
+
 \subsection{Scheduling Performance}
@@
 \subsection{Results Discussion}
-The previous results show that neural networks can approximate a scheduling algorithm for heterogeneous distributed systems, resulting in a significantly-good performance and fast execution.
+The previous results show that neural networks can approximate a scheduling algorithm for heterogeneous distributed systems, resulting in a significantly good performance and fast execution.
 The proposed network can perform well, even on unseen data it can produce efficient schedules.

### 2020-04-12 paper/core/exp_setup.tex
added discussion and results section
added abstract
added extra evaluation figure

@@
     \centering
-    \includegraphics[width=0.45\textwidth]{diagrams/framework}
-    \caption{The training framework of DeepSched network. A database of tasks and resources is provided for both network and HEFT. The loss of the network is measured based on HEFT produced schedule.}
+    \includegraphics[width=0.45\textwidth]{diagrams/train_framework}
+    \caption{The training framework of DeepSched network. A database of tasks and resources is provided to both network and HEFT. The loss of the network is measured based on HEFT produced schedule.}
     \label{fig:fw}
+\end{figure}
+
+\begin{figure}[hp]
+    \centering
+    \includegraphics[width=0.45\textwidth]{diagrams/eval_framework}
+    \caption{The evaluation framework of DeepSched network.
+A database of tasks and resources is provided to all three schedulers.
+The output schedules are passed to a simulation stub, which runs the schedules and calculates average turnaround time.}
+    \label{fig:efw}
 \end{figure}

### 2020-04-12 paper/core/exp_setup.tex
abstract and introduction review

@@
 \subsection{Evaluation}
+Fig.\ref{fig:efw} shows our evaluation framework of the network.
 The evaluation of our proposed method is conducted through running inference on both seen and unseen data of different lengths.

### 2020-04-12 paper/core/introduction.tex
added experimental setup section
abstract and introduction review

@@
-\IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) have driven our needs for better resource allocation methods.
+\IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) \cite{inproceedings} have driven our needs for better resource allocation methods.
 The performance of any system critically depends on the algorithms used to schedule tasks on its resources.
-These systems contain limited resources, that should be allocated properly, in order to perform the required tasks with maximum efficiency avoiding starvation and resource exhaustion.
+These systems contain limited resources that should be allocated properly, in order to perform the required tasks with maximum efficiency avoiding starvation and resource exhaustion.
 The general objective of any scheduling technique is to get the best possible performance with a reasonable resource utilization. \\
@@
 
-However, this comes with the problem of complex task scheduling.
+However, this comes with the problem of complex task scheduling process.
 The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system, because of the different execution rates of processors and different communication rates among different processors, which add extra layers of complexity to the problem.
@@
 
-The parameters of such problem make it very suitable for various optimization techniques.
+The first type of methods to turn to is greedy-based methods, where the best possible choice in the current situation is considered.
+The execution time of these methods rapidly increases with input size and their performance degrades in complex situations.
+However, the parameters of the scheduling problem in heterogeneous distributed systems make it very suitable for various optimization techniques.
 Recursive optimization techniques are very efficient in solving many optimization problem.
@@
 In this paper, we investigate the ability of advanced predictive models to learn a representation of static local task scheduling problem.
-This learned representation will be used to approximate the scheduling performance of other scheduling techniques.
+This learned representation is used to approximate the scheduling performance of other scheduling techniques.
 \emph{Neural Networks} are our best candidate for this task.
@@
 
-The recent advances in \emph{Deep Learning} research is considered in designing and training our scheduling network.
+The recent advances in \emph{Deep Learning} research are considered in designing and training our scheduling network.
 \emph{Heterogeneous Earliest Time First} (HEFT) \cite{993206} is used as a target, where the network learns to approximate its performance.

### 2020-04-12 paper/paper.tex
added future work
abstract and introduction review

@@
 The different execution time on different processors and different task dependencies make the scheduling problem very computationally intensive.
-Usually, researchers and developers turn to greedy-based methods or even recursive optimization methods to reach some optimal or sub-optimal solution.
+Usually, researchers and developers turn to greedy-based methods or even recursive optimization methods to reach some optimal or sub-optimal solutions.
 However, due to the nature of the problem, these solutions might take very long time and usually degrade in complex situations.
@@
 This makes neural networks a perfect candidate for us, however this comes at a cost of static scheduling scenarios, which is useful in some case such as simulation workflow on supercomputers.
-The proposed network can achieve almost the same performance of the approximated method (HEFT) on seen data during training and slightly worse performance on unseen data.
+The proposed network can achieve almost the same performance of the approximated method (HEFT) on seen data during training and slightly worse performance on unseen data with constant execution time at different input sizes.
 \end{abstract}
@@
 
-\section{Conclusion}
+\section{Conclusion and Future Work}
 \input{core/conclusion}
-
-\section{Future Work}
-\input{core/future_work}
 

### 2020-04-12 paper/core/related_work.tex
related work review

@@
 \subsection{Scheduling Categories}
-In this work, we focus on three basic categorization of heterogeneous task scheduling methods.
+In this work, we focus on three basic categorizations of heterogeneous task scheduling methods. \\
 
 \subsubsection{Application-Specific vs. System-Specific}
-Heterogeneous scheduling methods can be divided into two main categories based on their target metric.\\
+Heterogeneous scheduling methods can be divided into two main categories based on their target metric.
+
 \emph{Application-Specific} scheduling targets task execution speed (performance), where scheduling
 decisions are determined based on many parameters including application performance, task inter-dependency and the availability of resources.
-\emph{System-Specific} targets resource utilization, where scheduling decisions are based on the percentage of time a resource is available or busy.
+\emph{System-Specific} scheduling targets resource utilization, where scheduling decisions are based on the percentage of time a resource is available or busy.
+\\
 
@@
 Also, heterogeneous scheduling methods can be divided into global and local scheduling.
-\emph{Global} scheduling can migrate the tasks from one processor to another, meanwhile \emph{local} scheduling can't migrate, so once a task is assigned to a processor, it stays in its queue.
+
+\emph{Global} scheduling can migrate the tasks from one processor to another, meanwhile \emph{local} scheduling can't migrate, so once a task is assigned to a processor, it stays in its queue.  \\
 
@@
 Finally, heterogeneous scheduling methods can be divided into static and dynamic scheduling.
-In \emph{static} scheduling, the tasks required to be scheduled are defined before scheduling.
-However, in \emph{dynamic} scheduling, new tasks can be introduced during the scheduling process
+
+In \emph{static} scheduling, the tasks required to be scheduled are defined before scheduling. However, in \emph{dynamic} scheduling, new tasks can be introduced during the scheduling process
 
@@
 Each task has a running time for each different machine and a time for communicating the results to children tasks.
+HEFT is essentially a greedy algorithm, so it's unable make short-term sacrifices for long term benefits.
+Consequently, HEFT can fail in complex situations.
 A wide range of algorithms \cite{inbook} follows HEFT further improving the scheduling performance.
@@
 \subsection{Neural Networks}
-Recent advances in \emph{Deep Learning} have enabled neural networks to dominate many fields, such as computer vision, natural language processing and others.
+Recent advances in \emph{Deep Learning} have enabled neural networks to dominate many fields, such as computer vision, natural language processing, robotics and others.
 Neural networks are able to perform perception tasks at a human-level accuracy.
@@
 These properties make neural networks a perfect choice for massive scale automation of many tasks.
-Some studies even investigated the usage of \emph{Artificial Neural Networks} (ANN)\cite{article3} in task scheduling in heterogeneous systems.
+Some studies even investigated the usage of \emph{Artificial Neural Networks} (ANNs) \cite{article3} in task scheduling in heterogeneous systems.
 Most of these studies focus on the usage of \emph{Hopfield Nets} \cite{sathasivam2008logic} and \emph{Inhibitor Neurons} \cite{article3}.
@@
 
-In this paper, we make use of recent advances in \emph{Deep Learning} and build a deep representation of the scheduling problem and use it to approximate the performance of heterogeneous scheduling methods.
-\emph{Recurrent Neural Networks}(RNNs) \cite{chung2014empirical} are used for this purpose, as they have the ability to learn complex temporal information from a time-series data, which is exactly our case.
-Other network operations to be used, too.
+However, recent advances in \emph{Deep Learning} have come up with new techniques of using neural networks in complex situations.
+One of the most shiny techniques are \emph{Recurrent Neural Networks} (RNNs) \cite{chung2014empirical}.
+RNNs have been widely used in many fields such as natural language processing \cite{bahdanau2014neural}, speech recognition \cite{DBLP:journals/corr/AmodeiABCCCCCCD15}, image captioning \cite{DBLP:journals/corr/abs-1810-04020}, time-series prediction \cite{prasad2014deep} and others.
+They have proven to be very efficient in learning complex temporal information from time-series data.
+That's why, they are used with sequential data such as videos, speech and text.
+This makes RNNs our main choice, as we are dealing with sequential data which is the tasks to be scheduled.\\
+
+In this paper, we make use of recent advances in \emph{Deep Learning} such as RNNs and other techniques to learn a deep representation of the scheduling problem and use it to approximate the performance of heterogeneous scheduling methods.

### 2020-04-12 paper/core/methodology.tex
added abstract
added extra evaluation figure
methodology review

@@
+\begin{figure}[hp]
+    \centering
+    \includegraphics[width=0.45\textwidth]{diagrams/sched_nn}
+    \caption{The architecture of the proposed neural network (DeepSched) for distributed heterogeneous systems scheduling.}
+    \label{fig:nn}
+\end{figure}
+
 \subsection{Motivation}
@@
 
-In this work, we study the ability of neural networks to approximate some heuristic methods and explore its accuracy and execution time against heuristic and approximated methods.
+We study the ability of neural networks to approximate some heuristic methods and explore its accuracy and execution time against both heuristic and approximated methods.
 
@@
 We choose \emph{Heterogeneous Earliest Finish Time} (HEFT) \cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems.
-Also, genetic algorithms \cite{article2} is provided as an approximate baseline.
+Also, genetic algorithms \cite{article2} is provided as a baseline for approximate methods.
 \\
@@
 It has been used as a baseline in research due to its near-optimal results.
-Basically, it chooses some process to run on some machine, if the former has the earliest finish time, with considering the special nature of the heterogeneous system.
-However, HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process \\
+Basically, it's a greedy algorithm that chooses some process to run on some machine, if the former has the earliest finish time, with consideration of the special nature of the heterogeneous system.
+However, HEFT isn't practical for real-world systems, as the finish time of a process isn't usually known in advance.
+Also, the greedy nature of the HEFT scheduler makes it prone to failure in complex situations.
+\\
 
@@
 \end{equation}
+where \emph{N} is the number of tasks in the schedule, $W_t$ is the waiting time for a specific task.
 
@@
 \emph{Offline Optimization} of neural networks is to be used, in order to be able to train the network on scheduling samples and then use the trained network to do inference.
-We avoid using \emph{online optimization}, as it's slow and we mainly care about execution time of the scheduling method.
+We avoid using \emph{online optimization}, used in some fields such as neural style transfer \cite{gatys2015neural}.
+This is because it's slow and we mainly care about execution time of the scheduling method.
 
@@
 \\
-
-\begin{figure}[hp]
-    \centering
-    \includegraphics[width=0.45\textwidth]{diagrams/sched_nn}
-    \caption{The architecture of the proposed neural network (DeepSched) for distributed heterogeneous systems scheduling.}
-    \label{fig:nn}
-\end{figure}
 
@@
 
+Basically, the classifier is used during inference to produce the required schedule by determining the required machine for each task.
+However, the regressor is used at training along with the classifier, in order to add extra constraints on the network training and to enhance the loss function.
+This helps the network to learn a good representation of the scheduling problem and its parameters, also prevents the network from making some implicit mistakes in scheduling such as having two tasks executing on the same machine during the same range of time.
+\\
+
 \subsubsection{Objective Function}
 The cost function defined for this architecture is a sum of two criteria.
-Categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$.
-So it can be summarized as follows:
+The two criteria are categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$.
+So, it can be summarized as follows:
 \begin{equation}
@@
 \subsubsection{Drawbacks}
-The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network.
+The main drawback of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network.
 These numbers are used to define the network and loss function dimensions.
+So, the network design has to force some static scenarios to work on.

### 2020-04-12 paper/core/exp_setup.tex
experimental setup review

@@
 For execution time, we measure the total time consumed by scheduling different number of tasks.
-For scheduling performance, we measure the total turnaround time for all scheduled tasks.
+For scheduling performance, we measure the average turnaround time for all scheduled tasks.
 Our network is supposed to achieve better execution time with similar performance to HEFT on previously seen data and slightly lower performance on unseen data.
@@
 This module takes resource details as an input and learns a meaningful representation of them.
-It consists of one \emph{Conv1D} layer to extract the basic features of each processor, followed by one \emph{fully connected} layer to learn a compact representation of all processors, in order to be passed to the output modules.
+It consists of one \emph{Conv1D} \footnote{Convolution operation performed along one dimension only, usually used for regression.} layer to extract the basic features of each processor, followed by one \emph{fully connected} layer to learn a compact representation of all processors, in order to be passed to the output modules.
 The common input features for each processor passed to this module are number of processor cores, core frequency and memory capacity.
@@
 Cross-entropy is used as a classification loss and mean squared error (MSE) is used as a regression loss.
-The summation of the two losses \ref{eq:l} is used to train the network using gradient descent with \emph{Adam} optimizer and a learning rate of $1e$-$5$.
+The summation of the two losses \ref{eq:l} is used to train the network using gradient descent with \emph{Adam} optimizer and a learning rate of $1e$-$5$ with decay factor of $0.5$ every 20 epochs.
 The network is trained for $100$ epochs.
@@
 
-The training takes around $35$ minutes on \emph{Nvidia GTX} $1070$ and around $12$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance. \\
+The training takes around $35$ minutes on \emph{Nvidia GTX} $1070$ and around $10$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance. \\
 
@@
 Inference is performed on the trained network using both train and test data.
+We use some of the train data, in order to test the ability of the network on previously seen data against HEFT.
 We use the same $188$ resources information for all tests, however the input list of tasks is zero-padded to the maximum number of tasks, exactly like training.
@@
 This is done by passing the schedule produced by the three methods through a simple simulation that runs the proposed schedule and calculates the average turnaround time of all tasks.
-Evaluation is also conducted on the execution time of each scheduling method, as the speed of the scheduling algorithm is one of our main targets.
+Evaluation is also conducted on the execution time of each scheduling method, as the speed of the scheduling algorithm is one of our main concerns.

### 2020-04-12 paper/core/results.tex
results review

@@
 The proposed network shows almost the same average turnaround time as HEFT algorithm for the seen data during training.
-However, for unseen data, the network shows slightly more poor performance than HEFT, but still better than that of genetic algorithms.
+This is an indicator that the network can learn the underlying representation of the scheduling problem.
+However, this isn't enough, as the network needs to be tested on unseen data, too.
+For unseen data, the network shows slightly worse performance than HEFT, but still better than that of genetic algorithms.
+This indicates the ability of the network to generalize well to other inputs, as long as the network is provided by the same static scenarios and the same maximum number of tasks and resources.
+\\
 
 These results refer to the network ability to learn a good representation to the input machines and scheduling problem.
-The network performance degrades with high input sizes, as it's approximating HEFT, which is basically a greedy algorithm and prone to failure at complex situations.
+The network performance degrades with high input sizes, as it's approximating HEFT, which is basically a greedy algorithm and prone to failure at complex situations and large number of input tasks.
 Genetic algorithms shows similar behaviour too, due to large population size.
@@
 \begin{table}
-  \caption{Time comparison between the three discussed schedulers at different input sizes. Time measured in seconds.}
+  \caption{Time comparison between the three discussed schedulers at different input sizes. Time is measured in seconds.}
   \label{tab:exec_time}
@@
 GA time increases more rapidly than HEFT, as it's a recursive optimization method but HEFT is a greedy-based method.
+The performance and static execution time of the network in inference make the network very useful in the situations where static scheduling environment is provided.
 
@@
 However, this comes with a drawback of static scenarios.
-The neural network is trained with fixed input size, which is the maximum number of tasks, in our case.
+The neural network is trained with fixed input size, which is the maximum number of tasks and resources, in our case.
 At inference time, the input to the network can't exceed that number.
@@
 This gives neural networks a great potential to be a good task scheduler in static scenarios, where the maximum number of tasks and resources are known.
+The network can be trained offline and then deployed to perform task scheduling.
 However, in other dynamic scenarios, neural networks might not help much.

### 2020-04-12 paper/core/conclusion.tex
conclusion review and final format

@@
 However, the network can maintain a constant execution time at different input sizes, while HEFT execution time increases rapidly.
+Moreover, the trained network can outperform some recursive optimization techniques such as genetic algorithms both for seen and unseen data, as genetic algorithms can suffer from failures and long execution time due to random initialization and large population size.
 
@@
 They can learn good representation of the scheduling problem, while maintaining constant execution time in inference.
+So, neural networks can be a better choice than other techniques in certain scenarios.
 
@@
 Meanwhile, other solutions, such as RL solutions, can work well in a dynamic environment with no degradation with the complexity of the environment.
-This is important in IoT-based application, where the system is totally dynamic and can have different events.
+This is important in IoT-based application, where the system is totally dynamic and can have different unexpected events.
 
@@
 These methods aren't used in real life due to there time complexity.
-However, if these methods are approximated using neural networks, they can be deployed in real life applications.
+However, if these methods are approximated using neural networks, they can be deployed in real life applications achieving optimal or near-optimal performance.
+\\
 
-\emph{Second,} Other possible approximation methods can be tried through neural networks in order to confront dynamic scenarios.
-Online optimization can be one solution, however online network optimization can be very computationally-expensive.
+\emph{Second,} Other possible approximation methods can be tried through neural networks, in order to confront dynamic scenarios.
+Online optimization can be a solution for dynamic scenarios.
+However, online network optimization can be very computationally-expensive, as the network trains during inference optimizing its parameters to adapt to new inputs.
 Another possible solution is to use the proposed network as a function approximator in a \emph{Reinforcement Learning} (RL) environment, in order to be able to learn dynamically in case of new introduced tasks.
+\\
+
+The two previously mentioned methods can provide the proposed network with extra flexibility to be able to adapt and tune its parameters to learn from new unexpected inputs introduced through dynamic environments.

### 2020-04-15 paper/core/results.tex
small paper extension

@@
 The main advantage of using neural networks is constant inference time.
-Once the network is trained, it takes a static execution time in inference, as it's a simple feedforward process.
+Once the network is trained, it takes a static execution time in inference, as it's a simple feedforward process that highly supports operation parallelism.
 Table \ref{tab:exec_time} shows the execution time of the discussed schedulers at 3 different input sizes.
@@
 This is because the network is trained on the maximum input length.
+Also, neural networks operations are highly paralleled, which gives the network a very high speedup when dealing with simple feedforward process, such as network inference.
 However, HEFT and genetic algorithms execution time increases with input size.

### 2020-04-16 paper/paper.tex
small paper extension
conference format

@@
-\documentclass[twocolumn,11pt]{IEEEtran}
+\documentclass[conference,11pt]{IEEEtran}
+\IEEEoverridecommandlockouts
 \usepackage[verbose,expansion=alltext,stretch=50]{microtype}
@@
 \author{
-   \begin{tabular}{c| c| c| c}
-       Mohamed Shawky & Remonda Talaat & Mahmoud Adas & Evram Youssef\\
-       \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}} & \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}}
-   \end{tabular}%
-
-   \texttt{\small{\{mohamedshawky911, remondatalaat21, mido3ds, evramyousef\}@gmail.com}}
-}%
-
-\markboth{Cairo Uni. CMP Dep. $|$ OS Research $|$ Final Paper $|$ \today}{Shell}
+\IEEEauthorblockN{Mohamed Shawky}
+\IEEEauthorblockA{Computer Engineering\\
+Cairo University\\
+Email: mohamedshawky911@gmail.com} \\
+\IEEEauthorblockN{Remonda Talaat}
+\IEEEauthorblockA{Computer Engineering\\
+Cairo University\\
+Email: remondatalaat21@gmail.com}
+\and
+\IEEEauthorblockN{Mahmoud Adas}
+\IEEEauthorblockA{Computer Engineering\\
+Cairo University\\
+Email: mido3ds@gmail.com} \\
+\IEEEauthorblockN{Evram Youssef}
+\IEEEauthorblockA{Computer Engineering\\
+Cairo University\\
+Email: evramyousef@gmail.com}
+}
 
@@
 The complexity of neural networks comes at training time, however they can maintain constant execution time in inference.
-This constant execution time is relatively low, as it's a simple feedforward process.
+This constant execution time is relatively low, as it's a simple feedforward process that highly supports parallelism.
 This makes neural networks a perfect candidate for us, however this comes at a cost of static scheduling scenarios, which is useful in some case such as simulation workflow on supercomputers.

### 2020-04-16 paper/paper.tex
college mails

@@
 Cairo University\\
-Email: mohamedshawky911@gmail.com} \\
+Email: mohamed.sabae99@eng-st.cu.edu.eg} \\
 \IEEEauthorblockN{Remonda Talaat}
@@
 Cairo University\\
-Email: remondatalaat21@gmail.com}
+Email: Remonda.Bastawres99@eng-st.cu.edu.eg}
 \and
@@
 Cairo University\\
-Email: mido3ds@gmail.com} \\
+Email: mahmoud.ibrahim97@eng-st.cu.edu.eg} \\
 \IEEEauthorblockN{Evram Youssef}
@@
 Cairo University\\
-Email: evramyousef@gmail.com}
+Email: evram.narouz00@eng-st.cu.edu.eg}
 }
